---
title: "Data Analysis Script — How Children Engage with Adaptive AI Feedback"
author: "Lea Immenkamp"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: true
      smooth_scroll: true
    number_sections: true 
    global_numbering: true
    theme: flatly
editor_options: 
  markdown: 
    wrap: 72
---

# General Information

This R Markdown file documents the data analysis procedures for the
master thesis titled "How Children Engage with Adaptive AI Feedback:
Effects of Framing, Perception and Receptivity on Plan Quality
Improvement". It includes all steps required to prepare, describe, and
analyze the study data. The code is structured to be clear and
reproducible, with comments explaining the process. The analysis focuses
on understanding how different types of AI feedback (instructive vs.
dialogic) influence children’s plan quality improvement, motivation and
perceived helpfulness, while accounting for their receptivity of the
feedback.

```{r general-information-script, include=FALSE}
# This R Markdown file documents the data analysis procedures for the master thesis titled "How Children Engage with Adaptive AI Feedback: Effects of Framing, Perception and Receptivity on Plan Quality Improvement". It includes all steps required to prepare, describe, and analyze the study data. The code is structured to be clear and reproducible, with comments explaining the process. The analysis focuses on understanding how different types of AI feedback (instructive vs. dialogic) influence children’s plan quality improvement, motivation and perceived helpfulness, while accounting for their receptivity of the feedback.
```


# List of Tables

Data preparation

- Table \@ref(tab:package-management): R packages used in this analysis
- Table \@ref(tab:missing-data-documentation): Missing data

Codebook

- Table \@ref(tab:codebook): Codebook for Study Variables

Sample Characteristics

- Table \@ref(tab:sample-characteristics): Demographic characteristics of the sample

Distribution

- Table \@ref(tab:plan-quality-table): Distribution Scores for Initial and Revised Plan Quality
- Table \@ref(tab:perception-assumption-usefulness-table): Shapiro-Wilk Tests for Perceived Usefulness
- Table \@ref(tab:perception-test-usefulness): Wilcoxon Signed-Rank Tests for Perceived Usefulness

Descriptives

- Table \@ref(tab:descriptives): Descriptive Statistics by Feedback Condition

Hypotheses Testing

- Table \@ref(tab:RQ1-anova-trial-output): Model Comparison of trial random effect with Likelihood Ratio Test
- Table \@ref(tab:RQ1-anova-initial-pq-output): Model Comparison of initial plan quality with Likelihood Ratio Test
- Table \@ref(tab:RQ1-visualization-table): Linear Mixed Model Predicting Revised Plan Quality from Feedback Condition (H1)
- Table \@ref(tab:H2-1-visualization): Perceived Helpfulness as Mediator between Feedback Condition and Revised Plan Quality (H2.1)
- Table \@ref(tab:H2-2-visualization): Perceived Motivation as Mediator between Feedback Condition and Revised Plan Quality (H2.2)
- Table \@ref(tab:RQ3-visualization-table): Linear Mixed Model Testing the Moderating Role of Feedback Receptivity on Revised Plan Quality (H3)


Additional Analyses

- Table \@ref(tab:robust-RQ1-visualization): Cumulative Link Mixed Model of Plan Quality as a Function of Feedback Condition and Time Point (Robustness Check for H1)
- Table \@ref(tab:trial-anova-initial-table): Repeated Measures Anova for Initial Plan Quality across Trials
- Table \@ref(tab:trial-anova-revised-table): Repeated Measures Anova for Revised Plan Quality across Trials
- Table \@ref(tab:scenario-anova-initial-table): Repeated Measures Anova for Initial Plan Quality across Scenarios
- Table \@ref(tab:mixed-anova-gender-table): Mixed Anova of Plan Quality by Time and Gender
- Table \@ref(tab:robustness-check-RQ3-visualization): Model Comparison Receptivity: Original vs. Robustness Check (3-item)
- Table \@ref(tab:exploratory-RQ3-table): Exploratory Item-Level Moderation Analysis of Receptivity


  
# List of Figures 

Distribution

- Figure \@ref(fig:rubrics-visualization): Distribution of Scores Across Initial and Revised Rubric Items
- Figure \@ref(fig:spaghetti-plot): Spaghetti Plot on Child-level
- Figure \@ref(fig:spaghetti-plot-for-planning-trial): Spaghetti Plot on Trial-level
- Figure \@ref(fig:visualization-perception): Distribution of Perceived Helpfulness and Motivation
- Figure \@ref(fig:visualization-receptivity-plot): Distribution of Baseline Receptivity Items and Total Score


Hypotheses Testing

- Figure \@ref(fig:RQ1-visualization-plot): Estimated Marginal Means of Revised Plan Quality by Feedback Condition

Additional Analyses

- Figure \@ref(fig:plan-quality-across-trials): Trend in Plan Quality across Trials
- Figure \@ref(fig:plan-quality-across-scenarios): Plan Quality across Scenarios
- Figure \@ref(fig:mixed-anova-gender-figure): Plan Quality by Time and Gender



# Research Questions

**RQ1:** Does the change in children’s plan quality from the initial to
the revised plan differ between LLM-generated dialogic and instructive
feedback?

**RQ2:** To what extent does the perceived helpfulness and perceived motivation of LLM generated
feedback, mediate the relationship between feedback condition and children’s plan quality after revision, with the feedback being instructive vs. dialogic?

**RQ3:** Does feedback receptivity moderate the relationship between
LLM-generated instructive and dialogic feedback and the quality of the
revised plan?

# Data preparation

## Packages

```{r setup, include=FALSE}
# Set global chunk options for knitr
knitr::opts_chunk$set(
  echo      = FALSE, 
  # message   = FALSE,
  # warning   = FALSE,
  fig.align = "center",
  fig.width = 7,
  fig.height = 5
)


# load packages
library(tidyverse)
library(knitr)
library(kableExtra)
library(ordinal)
library(emmeans)
library(lmerTest)
library(performance)
library(r2glmm)
library(car)
library(lavaan)
library(lme4)
library(gt)
library(rstatix)
library(conflicted)
library(afex)
library(psych)
library(flextable)
library(officer)
library(DHARMa)
library(here)
library(renv)
library(janitor)

# Resolve namespace conflicts by specifying preferred functions from specific packages
conflicts_prefer(
  dplyr::select,
  dplyr::filter,
  dplyr::mutate,
  dplyr::summarise,
  dplyr::recode,
  dplyr::left_join,
  kableExtra::footnote
)

# Global seed ensures deterministic behavior for the whole document
set.seed(42)

# Named analysis constants 
N_bootstrap <- 5000                 # bootstrap replications for SEM mediation models
```

```{r renv-sync-check}
# Reproducibility check to verify that the local library matches the versions pinned in renv.lock
renv_status <- renv::status()

if (!isTRUE(renv_status$synchronized)) {
  warning(
    "renv library is out of sync with renv.lock.\n",
    "Run this once in the R console, then re-knit:\n\n",
    "    renv::restore()\n", # Restores exact package versions from the committed lockfile
    call. = FALSE
  )
}

```

```{r helper-function-formatting, include=FALSE}
# consistent p-value formatting
format_p <- function(p) {
  case_when(
    p < .001 ~ "< .001",
    TRUE ~ sub("^0", "", sprintf("%.3f", p))
  )
}

# consistent numeric formatting
fmt <- function(x, digits = 2) {
  sprintf(paste0("%.", digits, "f"), as.numeric(x))
}

# consistent numeric formatting
fmt_bounded <- function(x, digits = 3) {
  sub("^0\\.", ".", sprintf(paste0("%.", digits, "f"), as.numeric(x)))
}
```

```{r package-management}
# Create table of packages, their purpose and version 
packages <- data.frame(
  Package = c("tidyverse", "renv", "here", "janitor", "conflicted",
              "ordinal", "lme4", "lmerTest", "afex", "rstatix", "emmeans",
              "car", "performance", "r2glmm", "DHARMa", "lavaan",
              "psych",
              "knitr", "kableExtra", "gt",
              "flextable", "officer"),
  Purpose = c(
    "Data wrangling, transformation, and visualization",
    "precise version specification for reproducibility",
    "relative paths",
    "Cleaning messy data (variable names, empty rows/columns)",
    "Manage namespace conflicts",
    "Ordinal regression models",
    "Linear mixed-effects models (core functionality)",
    "Linear mixed-effects models with significance tests",
    "Analysis of factorial experiments and mixed models",
    "Statistical tests and effect sizes",
    "Estimated marginal means and post-hoc comparisons",
    "Companion to Applied Regression (diagnostics, Anova)",
    "Model diagnostics and assumption checking",
    "Semi-partial R² and Cohen's f² for fixed effects in mixed models",
    "Residual diagnostics for hierarchical and complex models",
    "Structural Equation Modeling (SEM)",
    "Psychometric analysis and descriptive statistics",
    "Dynamic document generation",
    "Table formatting for HTML and LaTeX",
    "Create formatted tables for publication",
    "Publication-ready table formatting and export",
    "Microsoft Office document generation and editing"
  )
)

# Read exact package versions from the committed lockfile (renv.lock)
lockfile <- renv::lockfile_read(here("renv.lock"))

locked_versions <- data.frame(
  Package = names(lockfile$Packages),
  Version = vapply(
    lockfile$Packages,
    function(pkg) pkg$Version %||% NA_character_,
    character(1)
  )
)

packages_with_versions <- dplyr::left_join(packages, locked_versions, by = "Package")

knitr::kable(
  packages_with_versions,
  format  = "html",
  caption = "R packages used in this analysis"
) |> 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

```{r load-data, include=FALSE}
# read the data
data_plan_and_feedback <- read_csv(here("data", "Plan_And_Feedback_GPT2.0_Thesis.csv"))
questionnaire        <- read_csv(here("data", "Questionnaire_GPT2.0_Thesis.csv"))
```

```{r merge-data, warning=FALSE}
# Remove fully blank rows (every column NA).
# As they contain no analyzable information, they are dropped here, prior to merging, so that the missing-data accounting reported below (see Missing Data section) reflects only substantive missingness within actual observations, not empty rows carried over from the raw file.
data_plan_and_feedback <- data_plan_and_feedback |>
  filter(if_any(everything(), ~ !is.na(.x)))

# Merge data sets and convert variable types
merged_data_raw <- data_plan_and_feedback |> 
  left_join(questionnaire, by = "child_id") |> 
  mutate(
    gender = as.factor(gender),
    scen_id = as.factor(scen_id),
    feedback_type = factor(feedback_type, levels = c("instructive", "dialogic")),
    initial_pq = as.numeric(initial_pq),
    revised_pq = as.numeric(revised_pq),
    pq_improvement = revised_pq - initial_pq,
    across(c(in_sp, in_ex, in_sa, in_ap, in_tp, 
             re_sp, re_ex, re_sa, re_ap, re_tp), as.integer)
  ) |>
  rename(
    receptivity = recep_total,
    feedback_condition = feedback_type
  )
```

```{r missing-data-documentation}
# Exclusion rule: children with more than 2 of 6 trials missing (initial_pq or revised_pq) are removed entirely, since such a high per-child missingness rate (>33%) would make within-person estimates (e.g. centering, random intercepts) unreliable.
max_missing_trials <- 2

n_children_before <- merged_data_raw |> distinct(child_id) |> nrow()
n_trials_before   <- nrow(merged_data_raw)

# Count missing trials per child
missingness_per_child <- merged_data_raw |>
  group_by(child_id) |>
  summarise(
    n_trials_total   = n(),
    n_trials_missing = sum(is.na(initial_pq) | is.na(revised_pq)),
    .groups = "drop"
  ) |>
  mutate(child_excluded = n_trials_missing > max_missing_trials)

# Identify children to exclude entirely
excluded_children <- missingness_per_child |>
  filter(child_excluded) |>
  pull(child_id)

n_children_excluded <- length(excluded_children)

# remove children with too many missing trials
# for remaining children, remove only the individual missing trials
merged_data <- merged_data_raw |>
  filter(!child_id %in% excluded_children) |>
  filter(!is.na(initial_pq), !is.na(revised_pq))

n_children_after <- merged_data |> distinct(child_id) |> nrow()
n_trials_after   <- nrow(merged_data)

# Trials dropped individually among retained children
n_trials_dropped_from_retained_children <- merged_data_raw |>
  filter(!child_id %in% excluded_children) |>
  filter(is.na(initial_pq) | is.na(revised_pq)) |>
  nrow()

n_trials_removed_via_child_exclusion <- merged_data_raw |>
  filter(child_id %in% excluded_children) |>
  nrow()


# Create a summary table of missing data
missing_data_table <- tibble::tibble(
  Level = c(
    "Children total",
    "Children excluded (> 2 of 6 trials missing)",
    "Children in final dataset",
    "",
    "Trials total",
    "Trials removed via child exclusion",
    "Trials removed individually (missing PQ, retained children)",
    "Trials in final dataset"
  ),
  n = c(
    as.character(n_children_before),
    as.character(n_children_excluded),
    as.character(n_children_after),
    "",
    as.character(n_trials_before),
    as.character(n_trials_removed_via_child_exclusion),
    as.character(n_trials_dropped_from_retained_children),
    as.character(n_trials_after)
  )
)

kableExtra::kbl(
  missing_data_table, 
  caption = "Missing data",
  col.names = c("Level", "n")) |>
  kableExtra::kable_styling(full_width = FALSE, font_size = 11) |>
  kableExtra::row_spec(3, extra_css = "border-bottom: 1px solid black;")
```

- Of the original `r n_children_before` children, `r n_children_excluded`
  (`r fmt(100 * n_children_excluded / n_children_before, 1)`%) was excluded
  because more than `r max_missing_trials` of its 6 trials had missing values in initial or revised plan quality. Among the
  remaining `r n_children_after` children, an additional
  `r n_trials_dropped_from_retained_children` individual trials with missing
  values were removed, resulting in <i>N</i> = `r n_trials_after` trials.

```{r missing-data-by-variable, include=FALSE}
vars_to_check <- c(
  "initial_pq", "revised_pq",
  "perct_help", "perct_moti",
  "recep_q1", "recep_q2", "recep_q3", "recep_q4_r", "receptivity",
  "age", "gender"
)

missing_by_variable <- merged_data |>
  summarise(across(all_of(vars_to_check), ~ sum(is.na(.x)))) |>
  pivot_longer(everything(), names_to = "Variable", values_to = "n_missing") |>
  mutate(Percent_missing = fmt(100 * n_missing / n_trials_after, 1))

kableExtra::kbl(
  missing_by_variable,
  caption = "Missing Data by Variable",
  col.names = c("Variable", "n missing", "% missing")
) |>
  kableExtra::kable_styling(full_width = FALSE, font_size = 11)
```

- All other variables are fully observed and have no missing values.

```{r data-preparation, cache=TRUE}
# Central variable preparation. All variables are centered and recoded here, so that the final dataset is ready for analysis.
merged_data <- merged_data |> 

   mutate(
    # within-person (cluster-mean) centering
    # subtract each child's own mean to isolate trial-to-trial variation from between-child differences
    perct_help_c = perct_help - mean(perct_help, na.rm = TRUE),
    perct_moti_c = perct_moti - mean(perct_moti, na.rm = TRUE),
    initial_pq_c = initial_pq - mean(initial_pq, na.rm = TRUE),
    .by = child_id                    
  ) |>
   
  mutate (
    # between-person component (child-level mean of initial plan quality) 
    initial_pq_mean_child = mean(initial_pq, na.rm = TRUE),
    .by = child_id
  ) |> 
 
   mutate(
    # grand-mean centering
    # the mean of baseline receptivity is taken on distinct child-level values first.
    receptivity_c = receptivity - 
      mean(distinct(pick(child_id, receptivity))$receptivity, na.rm = TRUE),

    # binary Dummy-coding for mediation models
    feedback_dummy = if_else(feedback_condition == "dialogic", 1, 0),

    # 3-Item-Receptivity without reverse-coded Item 4 (which has lower reliability), for robustness check 
    receptivity_3items = rowMeans(across(c(recep_q1, recep_q2, recep_q3)), na.rm = TRUE),

    # grand-mean centering of individual items for exploratory item-level moderation
    across(
      c(recep_q1, recep_q2, recep_q3, recep_q4_r),
      ~ .x - mean(distinct(pick(child_id, all_of(cur_column())))[[cur_column()]], na.rm = TRUE),
      .names = "{.col}_c"
    )
  )|> 
  mutate(
    # grand-mean centering for 3-item receptivity score, for robustness check. 
    receptivity_3items_c = receptivity_3items - 
      mean(distinct(pick(child_id, receptivity_3items))$receptivity_3items, na.rm = TRUE)
  )
```

```{r select-columns}
# arrange columns 
merged_data <- merged_data |>
  dplyr::select(
    child_id, trial_id,
    age, gender,
    scen_id, scen_name,
    feedback_condition,
    in_sp, in_ex, in_sa, in_ap, in_tp, initial_pq,
    re_sp, re_ex, re_sa, re_ap, re_tp, revised_pq,
    pq_improvement,
    perct_moti, perct_help, receptivity,
    starts_with("recep_q"),
    initial_pq_c, initial_pq_mean_child,
    everything()
  )
```

```{r helper-functions-lmm-table, include=FALSE}
# Helper function to extract fixed and random effects from a linear mixed model (lmer) and format them into a publication-ready table. The function takes the fitted model object and a named vector of term labels for more descriptive variable names.
extract_lmm_table <- function(model, term_labels) {
  coefs  <- summary(model)$coefficients
  ci_all <- confint(model, method = "profile")

  coef_tab <- tibble(
    Variable = rownames(coefs),
    Estimate = fmt(coefs[, "Estimate"]),
    SE       = fmt(coefs[, "Std. Error"]),
    t        = fmt(coefs[, "t value"]),
    p        = format_p(coefs[, "Pr(>|t|)"])
  )

  ci_tab <- tibble(
    Variable = rownames(ci_all),
    CI_low   = ci_all[, 1],
    CI_high  = ci_all[, 2]
  )

  fixed_part <- coef_tab |>
    dplyr::left_join(ci_tab, by = "Variable") |>
    dplyr::transmute(
      Effect = gsub("\\(Intercept\\)", "Intercept", Variable),
      Estimate, SE, LL = fmt(CI_low), UL = fmt(CI_high), t, p,
      Group = "Fixed Effects"
    )

  re <- as.data.frame(VarCorr(model))
  re$grp <- ifelse(re$grp == "child_id", "τ₀₀ (Intercept)", "σ² (Residual)")

  child_sd_ci    <- ci_tab[ci_tab$Variable == ".sig01", ]
  residual_sd_ci <- ci_tab[ci_tab$Variable == ".sigma", ]

  random_part <- tibble(
    Effect = re$grp, Estimate = fmt(re$vcov), SE = fmt(re$sdcor),
    LL = fmt(c(child_sd_ci$CI_low^2, residual_sd_ci$CI_low^2)),
    UL = fmt(c(child_sd_ci$CI_high^2, residual_sd_ci$CI_high^2)),
    t = "", p = "", Group = "Random Effects"
  )

  random_header <- tibble(
    Effect = "", Estimate = "Variance", SE = "SD",
    LL = "", UL = "", t = "", p = "", Group = "Random Effects"
  )

  table_out <- dplyr::bind_rows(fixed_part, random_header, random_part)
  matched_labels <- term_labels[table_out$Effect]
  table_out$Effect <- dplyr::coalesce(unname(matched_labels), table_out$Effect)
  table_out
}

render_lmm_gt <- function(table_data, caption, estimate_label = "b") {
  table_data |>
    gt(rowname_col = "Effect", groupname_col = "Group") |>
    tab_caption(caption = caption) |>
    cols_label(Estimate = md(paste0("*", estimate_label, "*")), SE = md("*SE*"), LL = md("*LL*"),
               UL = md("*UL*"), t = md("*t*"), p = md("*p*")) |>
    tab_spanner(label = "95% CI", columns = c(LL, UL)) |>
    cols_align(align = "center", columns = c(Estimate, SE, LL, UL, t, p)) |>
    cols_width(Effect ~ px(240), everything() ~ px(80)) |>
    opt_table_font(font = "Times New Roman") |>
    tab_style(style = cell_text(indent = px(20), align = "left"), locations = cells_stub()) |>
    tab_options(
      data_row.padding = px(8),
      column_labels.border.top.style = "solid", column_labels.border.top.width = px(1),
      column_labels.border.top.color = "black",
      column_labels.border.bottom.style = "solid", column_labels.border.bottom.width = px(1),
      column_labels.border.bottom.color = "black",
      table_body.border.bottom.style = "solid", table_body.border.bottom.width = px(1),
      table_body.border.bottom.color = "black",
      stub.border.style = "none"
    )
}
```


```{r helper-function-plot-theme, include=FALSE}
# Helper function for consistent ggplot theme for all thesis figures
theme_thesis <- function(base_size = 12, strip_face = "italic") {
  theme_minimal(base_family = "serif") +
    theme(
      legend.position = "none",
      axis.title.x = element_text(size = base_size, face = "bold", margin = margin(t = 10)),
      axis.title.y = element_text(size = base_size, face = "bold", margin = margin(r = 10)),
      axis.text    = element_text(size = base_size - 1),
      strip.text   = element_text(size = base_size, face = strip_face)
    )
}
```

```{r helper-function-effect-sizes, include=FALSE}
# Standardized effect sizes for fixed effects in a linear mixed model:
# Marginal/conditional R² (Nakagawa & Schielzeth, 2013): variance explained by fixed effects only vs. fixed + random effects.
# Semi-partial R² per fixed effect (Jaeger et al., 2016; "nsj" method, recommended for its low small-sample bias) and the corresponding Cohen's (1992) f², which quantifies the practical size of each effect's unique contribution.
extract_effect_sizes <- function(model) {
  r2_model <- performance::r2_nakagawa(model)

  r2beta_table <- r2glmm::r2beta(model, method = "nsj", partial = TRUE) |>
    as.data.frame() |>
    dplyr::transmute(
      Effect         = Effect,
      R2_semipartial = round(Rsq, 3),
      f2             = round(Rsq / (1 - Rsq), 3)
    )

  list(
    r2_marginal    = round(r2_model$R2_marginal, 3),
    r2_conditional = round(r2_model$R2_conditional, 3),
    per_predictor  = r2beta_table
  )
}
```

```{r helper-function-mediation-table, include=FALSE}
# Helper function to extract mediation effects from lavaan SEM output and formats them into a publication-ready table
extract_mediation_table <- function(fit_object, descriptions,
                                     labels = c("a", "b", "IDE", "DE", "TE")) {
  boot_estimates <- parameterEstimates(fit_object)
  std_estimates  <- standardizedSolution(fit_object)

  tibble(`Model Pathway & Effect` = descriptions, lbl = labels) |>
    rowwise() |>
    mutate(
      match_row = list(boot_estimates |> filter(label == .env$lbl)),
      match_std = list(std_estimates  |> filter(label == .env$lbl)),
      est  = match_row$est[1], beta = match_std$est.std[1],
      z    = match_row$z[1],   p    = match_row$pvalue[1],
      ll   = match_row$ci.lower[1], ul = match_row$ci.upper[1]
    ) |>
    ungroup() |>
    transmute(
      `Model Pathway & Effect`,
      b = fmt(est), beta = fmt(beta),
      `95% CI` = paste0("[", fmt(ll), ", ", fmt(ul), "]"),
      z = fmt(z), p = format_p(p)
)
}

render_mediation_kbl <- function(table_data, caption) {
  table_data |>
    kbl(align = c("l", "c", "c", "c", "c"),
        col.names = c("Model Pathway & Effect", "$b$", "$\\beta$", "95% CI", "$z$", "$p$"),
        caption = caption) |>
    kable_classic(full_width = FALSE, html_font = "Times New Roman") |>
    pack_rows("Component Pathways", 1, 2) |>
    pack_rows("Total Mediation Effects", 3, 5) |>
    column_spec(1, width = "8cm") |>
    column_spec(2:5, width = "2.5cm")
}
```

```{r helper-function-lmm-assumptions, include=FALSE}
# Helper function for full assumption-check battery for the linear mixed models H1 and H3. Both models share the same structure (lmer, single random intercept for child_id, a mix of categorical and continuous fixed effects), so the same complete set of checks applies to both. 
# Asummption tests that are not included in check_model() (see below) are added.
check_lmm_assumptions <- function(model, model_label, group_var = "child_id") {
  # Heteroscedasticity
  # statistical test (NCV/Breusch-Pagan-type)
  print(check_heteroscedasticity(model))

  # Residual pattern (DHARMa-Simulation)
  sim_res <- simulateResiduals(fittedModel = model, plot = FALSE)
  plotResiduals(sim_res)
  print(testResiduals(sim_res))

  # Normality of residuals 
  # statistical test (Shapiro-Wilk), for the same reason as heteroscedasticity above 
  print(check_normality(model))

  # Normality of random effects
  # an explicitly labeled QQ-plot per model kept separately since this computation is trivial and gives a clearly labeled, standalone plot
  re_effects <- ranef(model)[[group_var]][["(Intercept)"]]
  qqnorm(re_effects, main = paste("Q-Q Plot: Random Effects for", model_label))
  qqline(re_effects, col = "red")

  # Independence of residuals
  # autocorrelation test, plus ICC 
  print(check_autocorrelation(model))
  print(performance::icc(model))

  # Singular fit 
  # boundary estimate of random-effect variance
  print(check_singularity(model))

  # Multicollinearity among fixed effects
  print(check_collinearity(model))

  # Full visual diagnostic summary - adds linearity and influential observations, the only two checks not already covered above
  check_model(model)
}
```

```{r helper-function-mediation-assumptions, include=FALSE}
# Helper function to check assumptions for mediation analysis using linear models
check_mediation_assumptions <- function(mediator_model, outcome_model) {
  # 1. Normality of residuals (visual: QQ-plots, statistical: Shapiro-Wilk test on model residuals)
  plot(check_normality(mediator_model), type = "qq")
  plot(check_normality(outcome_model),  type = "qq")
  print(check_normality(mediator_model))
  print(check_normality(outcome_model))

  # 2. Homoscedasticity (DHARMa-Simulation, more robust for mixed models)
  sim_res_mediator <- simulateResiduals(fittedModel = mediator_model, plot = FALSE)
  sim_res_outcome  <- simulateResiduals(fittedModel = outcome_model,  plot = FALSE)
  # Visual: residuals vs. predicted, with quantile regression lines
  plotResiduals(sim_res_mediator)
  plotResiduals(sim_res_outcome)
  # Global checks
  print(testResiduals(sim_res_mediator))
  print(testResiduals(sim_res_outcome))

  # 3. No Omitted Confounders
  # Addressed theoretically/structurally by controlling for initial plan quality in the outcome model and the randomized within-subject assignment of feedback condition, which rules out most stable child-level confounds by design.

  # 4. Temporal Reversal handled by experimental temporal order.

  # Full visual diagnostic summary for both path models
  check_model(mediator_model)
  check_model(outcome_model)
}
```


# Codebook

```{r codebook}
# Create a codebook table for the study variables to provide clear definitions and descriptions for each variable used in the analysis. This table will serve as a reference for understanding the dataset and its components.
codebook_table <- tribble(
  ~Variable, ~Label, ~Description,
  "child_id", "Child ID", "Participant ID",
  "trial_id", "Trial ID", "Six trials (3 instructive, 3 dialogic)",
  "age", "Age", "Age of the participant",
  "gender", "Gender", "1 = Male, 2 = Female, 3 = Other",
  "scen_id", "Scenario ID", "Six different scenarios in randomized order",
  "scen_name", "Scenario Name", "Name/content of the scenario by trial",
  "feedback_condition", "Feedback Condition", "Instructive vs. dialogic feedback",
  "in_sp", "Initial Specificity", "Dummy-coded rubric for plan specificity (whether the plan precisely specifies a situational cue or a specific activity)",
  "in_ex", "Initial Externality", "Dummy-coded rubric for plan externality (whether the cue originates from the environment rather than internal states)",
  "in_sa", "Initial Salience", "Dummy-coded rubric for plan salience (whether the cue is sufficiently noticeable to trigger action)",
  "in_ap", "Initial Appropriateness", "Dummy-coded rubric for plan appropriateness (whether the context supports the initiation of the goal without major distractions)",
  "in_tp", "Initial Temporal Precision", "Dummy-coded rubric for temporal precision (the exactness of the timing regarding the situational trigger)",
  "initial_pq", "Initial Plan Quality", "Sum of five initial rubrics (0–5)",
  "re_sp", "Revised Specificity", "Dummy-coded rubric for plan specificity",
  "re_ex", "Revised Externality", "Dummy-coded rubric for plan externality",
  "re_sa", "Revised Salience", "Dummy-coded rubric for plan salience",
  "re_ap", "Revised Appropriateness", "Dummy-coded rubric for plan appropriateness",
  "re_tp", "Revised Temporal Precision", "Dummy-coded rubric for temporal precision",
  "revised_pq", "Revised Plan Quality", "Sum of five revised rubrics (0–5)",
  "pq_improvement", "Plan Quality Improvement", "Difference: revised_pq - initial_pq",
  "perct_moti", "Perceived Motivation", "Perceived motivation of feedback (1–4)",
  "perct_help", "Perceived Helpfulness", "Perceived helpfulness of feedback (1–4)",
  "recep_q1", "Receptivity Item 1", "Experiential attitudes subscale",
  "recep_q2", "Receptivity Item 2", "Instrumental attitudes subscale",
  "recep_q3", "Receptivity Item 3", "Cognitive engagement subscale",
  "recep_q4", "Receptivity Item 4", "Behavioral engagement subscale",
  "recep_q4_r", "Receptivity Item 4 (Reverse-coded)", "Reverse-coded behavioral engagement subscale",
  "receptivity", "Receptivity (Mean)", "Mean of 4 items (1–5)"
)

knitr::kable(
  codebook_table,
  format = "html",
  caption = "Codebook for Study Variables",
  escape = FALSE,
  align = c("l", "l", "l")
) |> 
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    font_size = 11
  ) |> 
  column_spec(1, width = "12em") |> 
  column_spec(2, width = "12em") |> 
  column_spec(3, width = "30em")

```

# Sample Characteristics

```{r sample-characteristics}
# Create a clean version of the questionnaire data that only includes participants present in the merged dataset
questionnaire_clean <- questionnaire |> 
  filter(child_id %in% merged_data$child_id)

# Create a summary table of demographic characteristics of the sample
n_summary <- questionnaire_clean |> 
  summarise(
    Characteristic = "Participants",
    Measure = "<i>N</i>",
    Value = as.character(n())
  )

age_summary <- questionnaire_clean |> 
  reframe(
    Characteristic = "Age (Year)",
    Measure = c("<i>Mean</i>", "<i>SD</i>", "<i>Min</i>", "<i>Max</i>"),
    Value = as.character(c(
      fmt(mean(age, na.rm = TRUE)),
      fmt(sd(age, na.rm = TRUE)),
      min(age, na.rm = TRUE),
      max(age, na.rm = TRUE)
    ))
  )

gender_summary <- questionnaire_clean |> 
  mutate(
    gender = dplyr::recode(as.character(gender),
      "1" = "Male",
      "2" = "Female",
      "3" = "Other"
    )
  ) |> 
  count(gender) |> 
  mutate(
    Percent = round(100 * n / sum(n), 1),
    Characteristic = "Gender",
    Measure = gender,
    Value = paste0(n, " (", Percent, "%)")
  ) |> 
  select(Characteristic, Measure, Value)

demographics_table <- dplyr::bind_rows(n_summary, age_summary, gender_summary)
demographics_table <- demographics_table |> 
  mutate(
    Characteristic = ifelse(duplicated(Characteristic), "", Characteristic)
  )

demographics_table |> 
  knitr::kable(
    align = "lcc",
    escape = FALSE,
    format = "html",
    caption = "Demographic Characteristics of the Sample"
  ) |> 
  kableExtra::kable_styling(
    full_width = FALSE,
    font_size = 11,
    html_font = "Times New Roman",
    bootstrap_options = c("condensed", "hover")  
  ) |> 
  kableExtra::row_spec(0, extra_css = "border-bottom: 1px solid black;") |>   
  kableExtra::row_spec(1:nrow(demographics_table),
  )        

```

# Distribution

Before conducting the analysis, the data distribution was inspected to
gain an understanding of the characteristics of the dataset.


## Distribution of Plan Quality Rubrics

```{r rubrics-distribution, include=FALSE}
# Extract rubric items
initial_items <- merged_data |> 
  select(in_sp, in_ex, in_sa, in_ap, in_tp)
revised_items <- merged_data  |> 
  select(re_sp, re_ex, re_sa, re_ap, re_tp)

# Descriptive Statistic
summary(initial_items)
print(sapply(initial_items, var)) 

summary(revised_items)
print(sapply(revised_items, var))
```

Plans (Initial and Revised) were rated on five dimensions:

- appropriateness
- externality
- salience
- specificity
- temporal precision

```{r rubrics-visualization, fig.cap="Distribution of Scores Across Initial and Revised Rubric Items"}
# Visualize the distribution of the five plan-quality rubric items (0/1) separately
# for initial and revised plans, to inspect item-level floor/ceiling effects that a
# single summed score (initial_pq/revised_pq) would otherwise mask
rubrics_visualization <- bind_cols(initial_items, revised_items) |>
  pivot_longer(cols = everything(), names_to = "item", values_to = "score") |>
  mutate(
    type = case_when(
      item %in% names(initial_items) ~ "Initial Plan",
      TRUE ~ "Revised Plan"
    ),
    type = factor(type, levels = c("Initial Plan", "Revised Plan")),
    item = recode_values(
      item,
      c("in_ap", "re_ap") ~ "appropriateness",
      c("in_ex", "re_ex") ~ "externality",
      c("in_sa", "re_sa") ~ "salience",
      c("in_sp", "re_sp") ~ "specificity",
      c("in_tp", "re_tp") ~ "temporal precision"
    )
  ) |>
  ggplot(aes(x = item, fill = factor(score))) +
  geom_bar(position = "dodge") +
  facet_wrap(~type, scales = "free_x", strip.position = "bottom") +
  labs(x = NULL, y = "Frequency", fill = "Score") +
  theme_thesis() +
  theme(
    legend.position = "right",
    axis.text.x = element_text(angle = 45, hjust = 1, size = 10),
    strip.placement = "outside",
    panel.spacing = unit(1, "lines")
  )
```

<small> *Note*. Bars show the frequency of plans meeting (1) or not
meeting (0) each rubric criterion. Initial Plan ratings were assigned
before feedback. Revised Plan ratings were assigned after feedback.
Frequencies are based on `r n_trials_after` observations for each rubric (`r n_children_after` children
× 6 trials - `r n_trials_dropped_from_retained_children` trial). </small>



```{r rubrics-scale-reliability, include=FALSE}
# Internal consistency of the initial/revised rubric scales (KR-20, since the five rubric items are dichotomously coded). Computed here, reported as inline text below the figure rather than as a standalone table, since only two numbers result.
alpha_initial <- psych::alpha(initial_items)
alpha_revised <- psych::alpha(revised_items)
```

- Internal consistency was acceptable for the initial plan quality
  scale (α = `r fmt_bounded(alpha_initial$total$raw_alpha, 2)`) but
  below the threshold of α = .70 (Nunnally, 1978) for the revised scale (α = `r fmt_bounded(alpha_revised$total$raw_alpha, 2)`),
  indicating comparatively lower reliability of the revised rubric items. Because the
  five items are dichotomously coded (0 = not met, 1 = met), Cronbach's alpha here is
  mathematically equivalent to the Kuder-Richardson Formula 20 (KR-20) coefficient
  (Kuder & Richardson, 1937).

## Distribution of Plan Quality

```{r plan-quality-descriptives, include=FALSE}
# Check ranges of plan quality scores 
range(merged_data$initial_pq, na.rm = TRUE) 
  table(merged_data$initial_pq)
range(merged_data$revised_pq, na.rm = TRUE) 
  table(merged_data$revised_pq)

initial_tab <- tabyl(merged_data$initial_pq) |> 
  adorn_pct_formatting(digits = 1) |> 
  mutate(initial = paste0(n, " (", percent, ")"))

revised_tab <- tabyl(merged_data$revised_pq) |> 
  adorn_pct_formatting(digits = 1) |> 
  mutate(revised = paste0(n, " (", percent, ")"))

colnames(initial_tab)[1] <- "score"
colnames(revised_tab)[1] <- "score"

final_tab <- full_join(initial_tab[, c("score", "initial")],
                       revised_tab[, c("score", "revised")],
                       by = "score") |> 
  arrange(as.numeric(as.character(score))) |> 
  mutate(across(everything(), ~replace(., is.na(.), "0 (0.0%)")))
```


```{r plan-quality-table}
kableExtra::kbl(
  final_tab,
  col.names = c("Score",
                "Initial PQ",
                "Revised PQ"),
  align = "c",
  caption = "Distribution Scores for Initial and Revised Plan Quality"
) |>
  kable_styling(
    font_size = 11,
    html_font = "Times New Roman"
  ) |>
  column_spec(1, width = "5em") |>
  column_spec(2, width = "8em") |>
  column_spec(3, width = "9em") |>
  row_spec(0:nrow(final_tab), extra_css = "line-height: 1.5; padding-top: 1px; padding-bottom: 1px;") |>
  kable_classic(full_width = FALSE, font_size = 12, html_font = "Times New Roman")

```

<small> *Note.* PQ= Plan Quality. Scores were calculated by summing the
five dichotomous rubric items (0 = criterion not met, 1 = criterion met)
for the initial and revised plans, resulting in a total score ranging
from 0 to 5. <i>N</i> = `r n_children_after` children, total observations =
`r n_trials_after` for initial and revised plan quality each. </small>


**Plan Quality Visualization**

Spaghetti plots showing the change in plan quality from pre- to
post-feedback, separately for instructive and dialogic feedback
conditions. A black line depicts the median improvement within each
feedback condition. Child-level and trial-level (see fig 2) plots are provided to visualize the data at different levels of aggregation.


```{r spaghetti-plot-for-planning-trial, fig.cap="Spaghetti Plot on Trial-level", warning=FALSE}
# Prepare data for plotting: each line represents a single planning trial, with points representing the initial and revised plan quality scores. This allows for visualization of the change in plan quality from pre- to post-feedback at the trial level.
spaghetti_data <- merged_data |> 
  dplyr::select(child_id, trial_id, feedback_condition, initial_pq, revised_pq) |> 
  tidyr::pivot_longer(
    cols = c(initial_pq, revised_pq),
    names_to = "Time",
    values_to = "Plan_Quality"
  ) |> 
  mutate(
    Time = recode_values (Time,
  "initial_pq" ~ "Pre-Feedback",
  "revised_pq" ~ "Post-Feedback"
  ),
    Time = factor(
      Time,
      levels = c("Pre-Feedback", "Post-Feedback")
    ),
    feedback_condition = factor(
      feedback_condition,
      levels = c("instructive", "dialogic"),
      labels = c("instructive Feedback", "dialogic Feedback")
    ),
    Trial_Group = paste(child_id, trial_id, sep = "_"),
    Participant = factor(child_id)
  ) |> 
  dplyr::filter(!is.na(feedback_condition), !is.na(Plan_Quality))

# create spaghetti plot with ggplot2
pq_trial_level <- ggplot(
  spaghetti_data,
  aes(x = Time, y = Plan_Quality, group = Trial_Group, color = Participant)
) +
  geom_line(alpha = 0.6, linewidth = 0.25) +
  geom_point(size = 0.8, alpha = 0.6) +
  stat_summary(
    fun = median,
    geom = "line",
    aes(group = 1),
    color = "black",
    linewidth = 0.8
  ) +
  stat_summary(
    fun = median,
    geom = "point",
    aes(group = 1),
    color = "black",
    size = 1
  ) +
  facet_wrap(~ feedback_condition, nrow = 1) +
  scale_y_continuous(breaks = 0:5, limits = c(0, 5)) +
   labs(
    x = "Time",
    y = "Plan Quality (0–5)") +
  theme_thesis() 


pq_trial_level
```

<small> *Note.* Each line in the plots represents a single planning
trial rather than an individual participant. As each child completed
multiple trials, several lines correspond to the same participant within
each feedback condition. The bold black line shows the median
improvement. </small>

## Distribution of Perceived Usefulness

Following each trial, participants evaluated the feedback regarding
perceived usefulness using four single-item measures on a four-point
Likert scale, with 1 indicating “not at all” and 4 indicating “very
helpful/ motivating”. Within this study perceived helpfulness and
perceived motivation were considered.

```{r visualization-perception-code, include=FALSE}
# Calculate within-person means for perceived helpfulness and motivation, separately for each feedback condition. This allows for visualization of the overall distributions of these perception scores across participants.
perception_within <- merged_data |> 
  dplyr::group_by(child_id, feedback_condition) |>  
  dplyr::summarise(
    Helpfulness_Mean   = mean(perct_help, na.rm = TRUE),
    Motivation_Mean    = mean(perct_moti, na.rm = TRUE),
    .groups = "drop"
  ) |> 
  mutate(
    feedback_condition = recode_values(
      feedback_condition,
      "instructive" ~ "instructive Feedback",
      "dialogic"    ~ "dialogic Feedback")
    )

perception_long <- perception_within |> 
  pivot_longer(
    cols = c(
      Helpfulness_Mean,
      Motivation_Mean
    ),
    names_to = "Perception_Type",
    values_to = "Score"
  ) |> 
  mutate(
    Perception_Type = recode_values(
      Perception_Type,
      "Helpfulness_Mean" ~ "Perceived Helpfulness",
      "Motivation_Mean" ~ "Perceived Motivation"
    ),
    feedback_condition = factor(
      feedback_condition,
      levels = c("instructive Feedback", "dialogic Feedback")
    )
  )
```


```{r visualization-perception, fig.cap="Distribution of Perceived Helpfulness and Motivation"}
# Create violin plots to visualize the distribution of participants’ within-person mean perception scores for each instructional condition, separately for perceived helpfulness and perceived motivation.
ggplot(
  perception_long,
  aes(x = feedback_condition, y = Score, fill = feedback_condition)
) +
  geom_violin(trim = FALSE, color = "black", alpha = 0.6) +
  geom_boxplot(
    width = 0.15,
    fill = "white",
    color = "black",
    outlier.shape = NA,
    linewidth = 0.6
  ) +
  facet_wrap(~ Perception_Type) +
  scale_y_continuous(breaks = 1:4) +
  coord_cartesian(ylim = c(1, 4)) +
  labs(
    x = "Feedback condition",
    y = "Perception Score"
  ) +
   theme_thesis() 
```

<small> *Note.* Each violin plot displays the distribution of
participants’ within-person mean perception scores for each
instructional condition. For each participant, perceived helpfulness and
motivation ratings were first averaged across the three trials within
each instructional condition. These aggregated within-person means were
then used to visualize the overall distributions. </small>



**Distributional Assumptions and Inferential Test for Helpfulness and
Motivation**

The assumption of normal distribution will be assessed using the
Shapiro–Wilk test. If the Shapiro–Wilk test indicates a significant
deviation from normality (<i>p</i> \< .05), the Wilcoxon signed-rank
test will be used for the differences in feedback condition. If the
assumption of normality is met (<i>p</i> ≥ .05), paired-samples t tests
will be conducted.

```{r perception-assumption-usefulness, include=FALSE}
# Prepare data for assumption checks and inferential tests by reshaping the perception data to a wide format, allowing for the calculation of difference scores between dialogic and instructive feedback conditions for perceived helpfulness and motivation.
perception_wide <- perception_within |> 
  mutate(
    feedback_condition = recode_values(
      feedback_condition,
      "instructive Feedback" ~ "instructive",
      "dialogic Feedback" ~ "dialogic"
    )
  ) |> 
  tidyr::pivot_wider(
    id_cols = child_id,
    names_from = feedback_condition,
    values_from = c(
      Helpfulness_Mean,
      Motivation_Mean
    )
  ) |> 
  mutate(
    help_diff = Helpfulness_Mean_dialogic - Helpfulness_Mean_instructive,
    moti_diff = Motivation_Mean_dialogic - Motivation_Mean_instructive
  )
```


```{r perception-assumption-usefulness-table}
# Check for normality of the difference scores for perceived helpfulness and perceived motivation using the Shapiro–Wilk test. If the p-value is less than 0.05, it indicates a significant deviation from normality, suggesting that non-parametric tests should be used for further analysis.
shapiro_help <- shapiro.test(na.omit(perception_wide$help_diff))
shapiro_moti <- shapiro.test(na.omit(perception_wide$moti_diff))

# Create a table summarizing the results of the Shapiro–Wilk tests for perceived helpfulness and perceived motivation, including the test statistic (W) and the p-value (formatted appropriately).
shapiro_table_h3 <- tibble::tibble(
  Outcome = c("Perceived Helpfulness", "Perceived Motivation"),
  Test = "Shapiro–Wilk",
  W = c(fmt(shapiro_help$statistic), fmt(shapiro_moti$statistic)),
  p = c(format_p(shapiro_help$p.value), format_p(shapiro_moti$p.value))
)

# Render the Shapiro–Wilk test results in a publication-ready table format using kableExtra, with appropriate alignment, caption, and column names.
shapiro_table_h3 |> 
  kbl(
    align = c("l", "l", "c", "c"), 
    escape = FALSE, 
    caption = "Shapiro-Wilk Tests for Perceived Usefulness",
    col.names = c("Outcome", "Test", "<i>W</i>", "<i>p</i>")  
  ) |> 
  kable_classic(full_width = FALSE, html_font = "Times New Roman")

```

- Perceived Helpfulness (*W* = `r fmt(shapiro_help$statistic, 3)`,
*p* `r format_p(shapiro_help$p.value)`) and Perceived Motivation
(*W* = `r fmt(shapiro_moti$statistic, 3)`, *p* `r format_p(shapiro_moti$p.value)`)
significantly deviated from a normal distribution. Therefore a Wilcoxon signed-rank test was performed.



```{r perception-test-usefulness}
# Conduct Wilcoxon signed-rank tests to compare perceived helpfulness and perceived motivation between dialogic and instructive feedback conditions, as the Shapiro–Wilk tests indicated that the assumption of normality was violated for both outcomes.
wilcox_help <- wilcox.test(
  perception_wide$Helpfulness_Mean_dialogic,
  perception_wide$Helpfulness_Mean_instructive,
  paired = TRUE,
  alternative = "two.sided"
)

wilcox_moti <- wilcox.test(
  perception_wide$Motivation_Mean_dialogic,
  perception_wide$Motivation_Mean_instructive,
  paired = TRUE,
  alternative = "two.sided"
)

help_long <- perception_wide |> 
  tidyr::pivot_longer(
    cols = c(
      Helpfulness_Mean_instructive,
      Helpfulness_Mean_dialogic
    ),
    names_to = "feedback_type",
    values_to = "helpfulness"
  )

wilcox_help_r <- rstatix::wilcox_effsize(
  data = help_long,
  formula = helpfulness ~ feedback_type,
  paired = TRUE
)

moti_long <- perception_wide |> 
  tidyr::pivot_longer(
    cols = c(
      Motivation_Mean_instructive,
      Motivation_Mean_dialogic
    ),
    names_to = "feedback_type",
    values_to = "motivation"
  )

wilcox_moti_r <- rstatix::wilcox_effsize(
  data = moti_long,
  formula = motivation ~ feedback_type,
  paired = TRUE
)

# Create a summary table of the Wilcoxon signed-rank test results for perceived helpfulness and perceived motivation, including the test statistic (V), p-value (formatted appropriately), and effect size (r).
wilcox_table_h3 <- tibble::tibble(
  Outcome = c("Perceived Helpfulness", "Perceived Motivation"),
  Test = "Wilcoxon signed-rank",
  V = c(
    as.numeric(wilcox_help$statistic),
    as.numeric(wilcox_moti$statistic)
  ),
   p = c(
     format_p(wilcox_help$p.value),
     format_p(wilcox_moti$p.value)
   ),
  effsize = c(
    fmt(wilcox_help_r$effsize), 
    fmt(wilcox_moti_r$effsize))
  )

# Render the Wilcoxon signed-rank test results in a publication-ready table format using kableExtra, with appropriate alignment, caption, and column names.
wilcox_table_h3 |> 
  kbl(
    align = c("l", "l", "c", "c", "c"), 
    escape = FALSE,
    caption = "Wilcoxon Signed-Rank Tests for Perceived Usefulness",
    col.names = c("Outcome", "Test", "<i>V</i>", "<i>p</i>", "Effect Size (<i>r</i>)")
  ) |> 
  kable_classic(full_width = FALSE, html_font = "Times New Roman")
```

<small> *Note.* Perceived Helpfulness and Perceived Motivation are compared
between dialogic feedback and instructive feedback conditions. </small>

- Wilcoxon signed-rank test revealed no statistically significant
  difference between conditions for perceived helpfulness and perceived
  motivation.

## Distribution of Receptivity

Feedback receptivity was measured prior to the planning trials. Ratings were collected on a 5-point Likert scale (1 =
not at all receptive, 5 = very receptive). 

```{r visualization-receptivity, include=FALSE}
# Prepare data for visualization of feedback receptivity items and total score by reshaping the data into a long format, allowing for the creation of violin plots to show the distribution of responses for each receptivity measure.
# Note: recep_q4_r is the reverse-coded item and needs to be included instead of the original recep_q4 item to ensure that all items are oriented in the same direction for analysis. Reverse encoding is derived from the raw CSV.
feedback_receptivity_long <- merged_data |> 
  distinct(child_id, .keep_all = TRUE) |>  
  pivot_longer(
    cols = c(recep_q1, recep_q2, recep_q3, recep_q4_r, receptivity),
    names_to = "Measure",
    values_to = "Score"
  ) |> 
  mutate(
    Measure = recode_values(
      Measure,
      "recep_q1"    ~ "Experiential Attitudes",
      "recep_q2"    ~ "Instrumental Attitudes",
      "recep_q3"    ~ "Cognitive Engagement",
      "recep_q4_r"  ~ "Behavioral Engagement",
      "receptivity" ~ "Feedback Receptivity"
    ),
    Measure = factor(
      Measure,
      levels = c(
        "Experiential Attitudes",
        "Instrumental Attitudes",
        "Cognitive Engagement",
        "Behavioral Engagement",
        "Feedback Receptivity"
      )
    )
  )
```


```{r visualization-receptivity-plot, fig.cap="Distribution of Baseline Receptivity Items and Total Score"}
# Create violin plots to visualize the distribution of participants’ responses for each feedback receptivity measure, including the four individual items and the overall mean score. Boxplots are overlaid to indicate medians and interquartile ranges.
ggplot(feedback_receptivity_long, aes(x = Measure, y = Score, fill = Measure)) +
  geom_violin(alpha = 0.4, adjust = 1.5, color = "darkgrey") +  
  geom_boxplot(width = 0.15, color = "black", alpha = 0.7, outlier.size = 1.5) + 
  scale_y_continuous(breaks = 1:5) +
  coord_cartesian(ylim = c(1, 5)) +
  labs(
    x = "Questionnaire Measure",
    y = "Rating (1-5)"
  ) +
  theme_thesis() +
  theme(
    plot.title    = element_text(size = 14, face = "bold", hjust = 0.5, margin = margin(b = 15)),
    axis.text.x   = element_text(size = 10, angle = 15, vjust = 0.7),
    panel.grid.minor = element_blank()
  )
```

<small> *Note.* Feedback Receptivity represents the mean of the four receptivity items. Violin plots show
response distributions and boxplots indicate medians and interquartile ranges. </small>

**Scale Reliability**

```{r receptivity-scale-reliability, include=FALSE}
# Prepare data for internal consistency analysis by selecting the four receptivity items, including the reverse-coded fourth item. This allows for the calculation of Cronbach's alpha to assess the reliability of the feedback receptivity scale.
receptivity_items <- merged_data[, c("recep_q1", "recep_q2", "recep_q3", "recep_q4_r")]

# Calculate Cronbach's alpha for the feedback receptivity scale using the psych package, which provides a measure of internal consistency reliability for the four items.
reliability_receptivity <- psych::alpha(receptivity_items)
print(reliability_receptivity)
```

- The overall scale reliability indicated a Cronbach's alpha of <i>α</i>
  = `r fmt(reliability_receptivity$total$raw_alpha, 2)`.
- Item-deletion diagnostics revealed that the reverse-coded fourth item
  retained a low corrected item-total correlation
  (<i>r</i> = `r fmt(reliability_receptivity$item.stats["recep_q4_r", "r.drop"], 2)`).
  Dropping this item optimized the scale's internal consistency to a
  marginally acceptable level
  (<i>α</i> = `r fmt(reliability_receptivity$alpha.drop["recep_q4_r", "raw_alpha"], 2)`; Nunnally, 1978).

# Summary Descriptives

```{r descriptives-preparation}
# Prepare a table with descriptive statistics for initial and revised plan quality ratings, improvement, motivation, helpfulness, and receptivity by feedback condition. The table includes means, standard deviations, medians, and interquartile ranges for each variable.
descriptives_table <- merged_data |> 
  group_by(feedback_condition) |> 
  summarise(
    `<i>N</i>` = as.character(n()),
    
    # Initial Plan Quality
    `Initial PQ_MSD` = paste0(fmt(mean(initial_pq, na.rm = TRUE)), " (", fmt(sd(initial_pq, na.rm = TRUE)), ")"),
    `Initial PQ_Med` = paste0(fmt(median(initial_pq, na.rm = TRUE)), " [", 
                           fmt(quantile(initial_pq, .25, na.rm = TRUE)), "–", 
                           fmt(quantile(initial_pq, .75, na.rm = TRUE)), "]"),
    
    # Revised Plan Quality
    `Revised PQ_MSD` = paste0(fmt(mean(revised_pq, na.rm = TRUE)), " (", 
                               fmt(sd(revised_pq, na.rm = TRUE)), ")"),
    `Revised PQ_Med` = paste0(fmt(median(revised_pq, na.rm = TRUE)), " [", 
                               fmt(quantile(revised_pq, .25, na.rm = TRUE)), "–", 
                               fmt(quantile(revised_pq, .75, na.rm = TRUE)), "]"),
    
    # Improvement
    `Improvement_MSD` = paste0(fmt(mean(revised_pq - initial_pq, na.rm = TRUE)), " (", 
                                fmt(sd(revised_pq - initial_pq, na.rm = TRUE)), ")"),
    `Improvement_Med` = paste0(fmt(median(revised_pq - initial_pq, na.rm = TRUE)), " [", 
                                fmt(quantile(revised_pq - initial_pq, .25, na.rm = TRUE)), "–", 
                                fmt(quantile(revised_pq - initial_pq, .75, na.rm = TRUE)), "]"),
    
    # Helpfulness
    `Helpfulness_MSD` = paste0(fmt(mean(perct_help, na.rm = TRUE)), " (", 
                                fmt(sd(perct_help, na.rm = TRUE)), ")"),
    `Helpfulness_Med` = paste0(fmt(median(perct_help, na.rm = TRUE)), " [", 
                                fmt(quantile(perct_help, .25, na.rm = TRUE)), "–", 
                                fmt(quantile(perct_help, .75, na.rm = TRUE)), "]"),
    
    # Motivation
    `Motivation_MSD` = paste0(fmt(mean(perct_moti, na.rm = TRUE)), " (", 
                               fmt(sd(perct_moti, na.rm = TRUE)), ")"),
    `Motivation_Med` = paste0(fmt(median(perct_moti, na.rm = TRUE)), " [", 
                               fmt(quantile(perct_moti, .25, na.rm = TRUE)), "–", 
                               fmt(quantile(perct_moti, .75, na.rm = TRUE)), "]"),
    
     # Receptivity
    `Receptivity_MSD` = paste0(fmt(mean(receptivity, na.rm = TRUE)), " (", 
                                fmt(sd(receptivity, na.rm = TRUE)), ")"),
    `Receptivity_Med` = paste0(fmt(median(receptivity, na.rm = TRUE)), " [", 
                                fmt(quantile(receptivity, .25, na.rm = TRUE)), "–", 
                                fmt(quantile(receptivity, .75, na.rm = TRUE)), "]"),
    
    .groups = "drop"
  ) |> 

  pivot_longer(
    cols = -c(feedback_condition, `<i>N</i>`),
    names_to = c("Variable", "Statistik"),
    names_sep = "_"
  ) |> 
  pivot_wider(
    names_from = Variable,
    values_from = value
  ) |> 
  mutate(
    Statistik = recode_values(
      Statistik, 
      "MSD" ~ "M (SD)", 
      "Med" ~ "Med [IPR]"),
    `<i>N</i>` = ifelse(Statistik == "Med [IPR]", "", `<i>N</i>`)
  ) |> 
  select(feedback_condition, Statistik, `<i>N</i>`, `Initial PQ`, `Revised PQ`, Improvement, Helpfulness, Motivation, Receptivity) |> 
  rename(`Feedback condition` = feedback_condition, `Metric` = Statistik)
```

```{r descriptives}
# Render the descriptive statistics table in a publication-ready format using kableExtra, with appropriate alignment, caption, and column specifications. The table presents means (M), standard deviations (SD), medians, and interpercentile ranges (IPR) for each variable by feedback condition.
kbl(descriptives_table, 
    escape = FALSE,  
    caption = "Descriptive Statistics by Feedback Condition",
    align = c("l", "l", "c", "c", "c", "c", "c", "c", "c")) |> 
  kable_styling(
    full_width = FALSE,
    font_size = 11,
    html_font = "Times New Roman"
  ) |> 
  column_spec(1, width = "12em") |> 
  column_spec(2, width = "8em") |> 
  column_spec(3:9, width = "12em", extra_css = "text-align: center;") |> 
  collapse_rows(columns = 1:3, valign = "top")

```

<small> *Note.* PQ = Plan
Quality. IPR = Interpercentile range (25th–75th percentile). Initial and Revised Plans
were evaluated across five plan-quality dimensions. Each dimension was
scored dichotomously (0 = criterion not met, 1 = criterion met). The
scores were summed to create a total plan-quality score ranging from 0
to 5. Improvement was calculated as the difference between revised and
initial plan quality scores. Perceived Helpfulness/Motivation and
Receptivity are based on participants’ within-person mean scores
aggregated across the three trials within each Feedback condition.
Perception ratings ranged from 1 (“not at all”) to 4 (“very helpful” /
“very motivating”). Receptivity ratings ranged from 1 (“not at all
receptive”) to 5 (“very receptive”)." </small>

# Hypotheses Testing

## Research Question 1

**RQ1:** Does the change in children’s plan quality from the initial to
the revised plan differ between LLM-generated dialogic and instructive
feedback?

**H1:** Children show higher revised plan quality after dialogic
feedback than after instructive feedback, controlling for their initial
plan quality.

**Planned Analysis:** To test the hypothesis, a linear mixed-effects model will be fitted with revised plan quality as the dependent variable, feedback condition as the fixed effect, and initial plan quality as a covariate. A random intercept for child will be included to account for the nested structure of the data (multiple trials per child). Two additional models will be fitted including a random intercept for trial to account for potential variability across different trials and a model that decomposes initial plan quality into within-person centered and between-person mean components to account for potential confounding effects of individual differences in initial plan quality. The models will be compared using a likelihood ratio test to determine if the inclusion of the variables significantly improves model fit. Estimated marginal means will be calculated to examine the effect of feedback condition on revised plan quality while controlling for initial plan quality.
Age and gender were not entered as covariates because feedback condition was manipulated within child, making between-child confounds unlikely to explain the contrast. 

**RQ1 Results of Assumption Testing**

- Non-Linearity detected
- Heteroscedasticity detected
- Non-normality of residuals detected
- Independence of residuals ✓
- Normality of random effects ✓
- *Conclusion:* Data does not meet all assumptions for analysis (full diagnostic output and test statistics reported in the
  Appendix).
  Although linear mixed-effects models demonstrate high robustness to
  heteroscedasticity and non-normality of residuals, a robustness check
  will be performed in the end. 

✓ = assumption met

**Anova for Model Comparison**

Models with and without random intercept for trial were compared to determine if the inclusion of the trial random effect significantly improves model fit. If the p-value from the likelihood ratio test is greater than 0.05, the simpler model without the trial random effect will be used for further analysis.

**Model specification**

```{r RQ1-model-comparison-trial, results='hide', echo=TRUE}
# fit linear mixed model to test differences between feedback conditions, control for initial plan quality and consider random intercept for child
model_h1_raw <- lmerTest::lmer(
  revised_pq ~ feedback_condition + initial_pq + (1 | child_id),
  data = merged_data
) 


# fit linear mixed model to test differences between feedback conditions, control for initial plan quality and consider random intercept for child and trial
model_with_trial <- lmerTest::lmer(
  revised_pq ~ feedback_condition + initial_pq + (1 | child_id) + (1 | trial_id),
  data = merged_data
)
```

```{r RQ1-anova-trial, include=FALSE}
# compare models with and without random intercept for trial
trial_anova <- anova(model_h1_raw, model_with_trial)

# Create a data frame to summarize the model comparison results, including AIC, BIC, Chi-squared statistic, and p-value for the likelihood ratio test. 
comparison_trial <- data.frame(
  Model = c("Raw Model", "Controlled for trial id"),
  AIC = fmt(trial_anova$AIC),
  BIC = fmt(trial_anova$BIC),
  "Chisq" = c("", fmt(trial_anova$Chisq[2])),
  "p-value" = c("", format_p(trial_anova$`Pr(>Chisq)`[2]))
)

```

```{r RQ1-anova-trial-output}
# Render the model comparison results in a publication-ready table format using kableExtra, with appropriate alignment, caption, and column specifications. The table presents AIC, BIC, Chi-squared statistic, and p-value for the likelihood ratio test comparing models with and without the trial random effect.
kableExtra::kbl(
  comparison_trial,
  caption = "Model Comparison of trial random effect with Likelihood Ratio Test"
) |> 
  kable_classic(
    full_width = FALSE, 
    html_font = "Times New Roman"
  ) |> 
  column_spec(1:5, extra_css = "padding: 10px;") |> 
  row_spec(0, extra_css = "text-align: center;")

# Decision on model selection based on p-value from likelihood ratio test
if ((trial_anova)$`Pr(>Chisq)`[2] > 0.05) {
  print("The model without the trial random effect is sufficient for analysis.")
} else {
  print("The model with the trial random effect provides a significantly better fit and will be used for further analysis.")
}
```

A Model that decomposes initial plan quality into within-person centered and between-person mean components was also compared with the model that uses raw initial plan quality as covariate. If the p-value from the likelihood ratio test is greater than 0.05, the simpler model with raw initial plan quality will be used for further analysis.

```{r RQ1-model-comparison-initial-pq, results='hide', echo=TRUE}
# Decompose initial plan quality into within-person centered and between-person mean components to account for potential confounding effects of individual differences in initial plan quality on the relationship between feedback condition and revised plan quality.
model_h1_decomp <- lmerTest::lmer(
  revised_pq ~ feedback_condition + initial_pq_c + initial_pq_mean_child + (1 | child_id),
  data = merged_data
)
```

```{r RQ1-anova-initial-pq, include=FALSE}
# compare models with and without decomposed initial plan quality to determine if the decomposition significantly improves model fit. 
initial_pq_anova <- anova(model_h1_decomp, model_h1_raw)

# Create a data frame to summarize the model comparison results, including AIC, BIC, Chi-squared statistic, and p-value for the likelihood ratio test. 
comparison_initial_pq <- data.frame(
  Model = c("Raw Model", "Decomposed initial plan quality"),
  AIC = fmt(initial_pq_anova$AIC),
  BIC = fmt(initial_pq_anova$BIC),
  "Chisq" = c("", fmt(initial_pq_anova$Chisq[2])),
  "p-value" = c("", format_p(initial_pq_anova$`Pr(>Chisq)`[2]))
)

```

```{r RQ1-anova-initial-pq-output}
# Render the model comparison results in a publication-ready table format using kableExtra, with appropriate alignment, caption, and column specifications. The table presents AIC, BIC, Chi-squared statistic, and p-value for the likelihood ratio test comparing models with and without initial plan quality decomposition.
kableExtra::kbl(
  comparison_initial_pq,
  caption = "Model Comparison of initial plan quality with Likelihood Ratio Test"
) |> 
  kable_classic(
    full_width = FALSE, 
    html_font = "Times New Roman"
  ) |> 
  column_spec(1:5, extra_css = "padding: 10px;") |> 
  row_spec(0, extra_css = "text-align: center;")

# Decision on model selection based on p-value from likelihood ratio test
if ((initial_pq_anova)$`Pr(>Chisq)`[2] > 0.05) {
  print("The model without the decomposed initial plan quality is sufficient for analysis.")
} else {
  print("The model with the decomposed initial plan quality provides a significantly better fit and will be used for further analysis.")
}
```


```{r RQ1-model}
# Fit the final linear mixed-effects model for H1, using the decomposed initial plan quality as covariates and including a random intercept for child. This model will be used for further analysis and interpretation of the effects of feedback condition on revised plan quality.
model_h1 <- lmerTest::lmer(
  revised_pq ~ feedback_condition + initial_pq_c + initial_pq_mean_child + (1 | child_id),
  data = merged_data
)
```

**ICC and effect sizes for final model**

```{r RQ1-effect-sizes}
# Intraclass correlation coefficient to examine the proportion of variance explained by the random effect of child
performance::icc(model_h1)

# Calculate effect sizes for the linear mixed model, including marginal and conditional R² values, as well as semi-partial R² and f² for each predictor. This provides insight into the variance explained by fixed effects alone and by both fixed and random effects combined.
effect_sizes_h1 <- extract_effect_sizes(model_h1)
effect_sizes_h1$r2_marginal      # variance explained by fixed effects
effect_sizes_h1$r2_conditional   # variance explained by fixed + random effects
effect_sizes_h1$per_predictor    # semi-partial R² and f² per predictor
```


```{r RQ1-visualization-table, message=FALSE}
# Create a summary table of the linear mixed model results for H1, including estimates, standard errors, t-values, p-values, and confidence intervals for each predictor. The table is formatted for publication using the gt package.
table_h1 <- extract_lmm_table(model_h1,c(
  "Intercept" = "Intercept",
  "feedback_conditiondialogic" = "Feedback Condition (Dialogic)",
  "initial_pq_c" = "Initial PQ (Trial-Level)",
  "initial_pq_mean_child" = "Initial PQ (Child-Level)"
))
render_lmm_gt(table_h1, caption = "Linear Mixed Model Predicting Revised Plan Quality from Feedback Condition (H1)")
```
<small> *Note.* <i>N</i> = `r n_children_after` children, total observations =
`r n_trials_after` trials. Instructive feedback serves as the reference
category for feedback condition. PQ = Plan Quality. CI = confidence interval; <i>LL</i> =
lower limit; <i>UL</i> = upper limit. 
R²m = `r fmt_bounded(effect_sizes_h1$r2_marginal)`,
R²c = `r fmt_bounded(effect_sizes_h1$r2_conditional)`. </small>


```{r RQ1-visualization-plot, fig.cap="Estimated Marginal Means of Revised Plan Quality by Feedback Condition"}
# Calculate estimated marginal means for revised plan quality by feedback condition using the emmeans package, and visualize the results with ggplot2, including point estimates and confidence intervals.
emm <- emmeans::emmeans(model_h1, "feedback_condition")
emm |>  
  as.data.frame() |>  
  ggplot(aes(feedback_condition, emmean)) +
  geom_point() +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = .1) +
  theme_minimal() +
  labs(
   x = "Feedback condition",
    y = "Estimated Revised Plan Quality"
  )
```
<small> *Note.* Estimated marginal means of revised plan quality are adjusted for initial plan quality (trial-level and child-level) and represent the expected revised plan quality for each feedback condition. Error bars indicate 95% confidence intervals. 
</small>

## Research Question 2

**RQ2:** To what extent does the perceived usefulness of LLM generated
feedback, specifically perceived helpfulness and perceived motivation,
mediate the relationship between feedback condition and children’s plan
quality after revision, with the feedback being instructive vs.
dialogic?

**H2.1:** The perceived helpfulness of the feedback mediates the
relationship between LLM-generated feedback condition and the quality of
children's revised plans. Specifically, dialogic feedback will lead to a
different perceived usefulness than instructive feedback, which in turn
will predict a different plan quality after revision.

**H2.2:** The perceived motivation of the feedback mediates the
relationship between LLM-generated feedback condition and the quality of
children's revised plans. Specifically, dialogic feedback will lead to a
higher perceived motivation, than instructive feedback, which in turn
will predict a higher plan quality after revision.

**Planned Analysis:** To test these hypotheses, a mediation analysis will be conducted using the `lavaan` package. The analysis will examine the indirect effects of feedback condition on revised plan quality through perceived helpfulness and perceived motivation, while controlling for initial plan quality. Bootstrapping will be used to obtain confidence intervals for the indirect effects, given the potential violations of normality and heteroscedasticity assumptions. The mediation model will include feedback condition as the independent variable, perceived helpfulness / perceived motivation as mediators, and revised plan quality as the dependent variable. The analysis will also account for the clustered nature of the data by including a random intercept for child.

**RQ2, H2.1 Results of Assumption Testing**

- Non-Linearity of Path Relations detected
- Non-normality of residuals detected
- Heteroscedasticity detected
- No Omitted Confounders ✓ (Theoretically assumed)
- *Conclusion:* Data does not meet all assumptions for analysis (full diagnostic output and test statistics reported in the
  Appendix).
  Deviations could reflect the bounded categorical nature of the scores,
  which is why a Bootstrapping was performed

✓ = assumption met

**Model specification**

```{r RQ2-H2-1-model, results='hide', echo=TRUE, cache=TRUE}
# specify mediation model with feedback condition as independent variable, perceived helpfulness as mediator and revised plan quality as dependent variable, controlling for initial plan quality
# perct_help is within-person centered specifically because feedback_condition is manipulated within each child
# Initial plan quality is entered as separate within-child (initial_pq_c) and between-child (initial_pq_mean_child) components, consistent with H1. 
mediation_model <- '
  # Path a (Effect of binary feedback condition on continous Mediator) 
  perct_help_c ~ a * feedback_dummy

 # Path b und c\' (Effect of continous Mediator and binary feedback condition on "continous" Outcome, controlling for initial plan quality)
  revised_pq ~ b * perct_help_c + cp * feedback_dummy + initial_pq_c + initial_pq_mean_child

  IDE := a * b          
  DE  := cp             
  TE  := DE + IDE       
'

```

```{r RQ2-H2-1-bootstrap, include=FALSE, cache=TRUE, dependson = c("data-preparation", "RQ2-H2-1-model")}
# Cluster correction for child_id and Bootstrap to handle the non-normal distribution of error terms
set.seed(42) #fixed to ensure reproducible Bootstrap resampling results
fit_h21 <- sem(model = mediation_model, 
           data = merged_data, 
           cluster = "child_id",
           se = "bootstrap",    
           bootstrap = N_bootstrap)    

summary(fit_h21, standardized = TRUE, ci = TRUE)

# Explained variance (R²) of the mediator and outcome equations for H2.1 
r2_h21 <- lavInspect(fit_h21, "rsquare")
r2_h21
```


```{r H2-1-visualization}
# Create a summary table of the mediation analysis results for H2.1, including estimates, standard errors, z-values, p-values, and confidence intervals for each path in the mediation model. The table is formatted for publication using the gt package.
table_h2_1 <- extract_mediation_table(fit_h21, 
descriptions = c(
  "Path a (Condition -> Helpfulness)",
  "Path b (Helpfulness -> Revised Quality)",
  "Indirect Effect (IDE)", "Direct Effect (DE / Path c')", "Total Effect (TE)"
))
render_mediation_kbl(table_h2_1, caption = "Perceived Helpfulness as Mediator between Feedback Condition and Revised Plan Quality (H2.1)")
```

<small> *Note.* Instructive feedback serves as the reference category for
feedback condition. Perceived helpfulness serves as Mediator and was
centered as well as the covariate. <i>b</i> = unstandardized estimate;
<i>𝛽</i> = standardized estimate. 95% CI bounds correspond to
unstandardized effects (calculated via cluster bootstrap at the child
level). <i>R²</i><sub>mediator</sub> = `r fmt_bounded(r2_h21["perct_help_c"])`,
<i>R²</i><sub>outcome</sub> = `r fmt_bounded(r2_h21["revised_pq"])`. </small>



**RQ2, H2.2 Results of Assumption Testing**

- Non-Linearity of Path Relations detected

- Non-normality of residuals detected

- Heteroscedasticity detected

- No Omitted Confounders ✓ (Theoretically assumed)

- *Conclusion:* Data does not meet all assumptions for analysis.
  Deviations could reflect the bounded categorical nature of the scores,
  which is why a Bootstrapping will be performed

**Model specification**

```{r RQ2-H2-2-model, results='hide', echo=TRUE, cache=TRUE}
# specify mediation model with feedback condition as independent variable, perceived motivation as mediator and revised plan quality as dependent variable, controlling for initial plan quality
# perct_moti is within-person centered specifically because feedback_condition is manipulated within each child
# Initial plan quality is entered as separate within-child (initial_pq_c) and between-child (initial_pq_mean_child) components, consistent with H1. 
mediation_model_h2 <- '
  # Path a (Effect of binary feedback condition on continous Mediator) 
  perct_moti_c ~ a * feedback_dummy

  # Path b und c\' (Effect of continous Mediator and binary feedback condition on "continous" Outcome, controlling for initial plan quality)
  revised_pq ~ b * perct_moti_c + cp * feedback_dummy + initial_pq_c + initial_pq_mean_child

  IDE := a * b          
  DE  := cp             
  TE  := DE + IDE       
'
```

```{r RQ2-H2-2-bootstrap, include=FALSE, cache=TRUE, dependson = c("data-preparation", "RQ2-H2-2-model")}
# Cluster correction for child_id and Bootstrap to handle the non-normal distribution of error terms
set.seed(42)
fit_h22 <- sem(model = mediation_model_h2, 
           data = merged_data, 
           cluster = "child_id",
           se = "bootstrap",    
           bootstrap = N_bootstrap)    

summary(fit_h22, standardized = TRUE, ci = TRUE)

# Explained variance (R²) of the mediator and outcome equations for H2.2
r2_h22 <- lavInspect(fit_h22, "rsquare")
r2_h22
```


```{r H2-2-visualization}
# Create a summary table of the mediation analysis results for H2.2, including estimates, standard errors, z-values, p-values, and confidence intervals for each path in the mediation model. The table is formatted for publication using the gt package.
table_h2_2 <- extract_mediation_table(fit_h22, descriptions = c(
  "Path a (Condition -> Motivation)",
  "Path b (Motivation -> Revised Quality)",
  "Indirect Effect (IDE)", "Direct Effect (DE / Path c')", "Total Effect (TE)"
))
render_mediation_kbl(table_h2_2, caption = "Perceived Motivation as Mediator between Feedback Condition and Revised Plan Quality (H2.2)")
```
<small> *Note.* Instructive feedback serves as the reference category for
feedback condition. Perceived helpfulness serves as Mediator and was
centered as well as the covariate. <i>b</i> = unstandardized estimate;
<i>𝛽</i> = standardized estimate. 95% CI bounds correspond to
unstandardized effects (calculated via cluster bootstrap at the child
level). <i>R²</i><sub>mediator</sub> = `r fmt_bounded(r2_h22["perct_moti_c"])`,
<i>R²</i><sub>outcome</sub> = `r fmt_bounded(r2_h22["revised_pq"])`. </small>


## Research Question 3

**RQ3:** Does feedback receptivity moderate the relationship between
LLM-generated instructive and dialogic feedback and the quality of the
revised plan?

**H3:** Feedback receptivity moderates the relationship between
LLM-generated instructive and dialogic feedback and the quality of the
revised plan.

**Planned Analysis:** To test this hypothesis, a linear mixed model will
be fitted with revised plan quality as the dependent variable, feedback
condition, receptivity and their interaction as fixed effects,
controlling for initial plan quality, and a random intercept for child
to account for the repeated measures design. The significance of the
interaction term will be examined to determine if the relationship
between feedback condition and revised plan quality differs based on
children’s receptivity to the feedback.

**RQ3 Results of Assumption Testing**

- Non-Linearity detected
- Heteroscedasticity detected
- Non-normality of residuals detected
- Normality of random effects ✓
- No multicollinearity ✓
- *Conclusion:* Data does not meet all the assumptions for analysis (full diagnostic output and test statistics reported in the
  Appendix). Thus, a robustness check will be performed in the end to examine the robustness of the receptivity scale's internal
  consistency.
  
✓ = assumption met

**Model specification**

```{r RQ3-model, results='hide', echo=TRUE}
# fit linear mixed model with interaction between feedback condition and receptivity, controlling for initial plan quality and random intercept for child
model_h3 <- lmerTest::lmer(
  revised_pq ~ feedback_condition * receptivity_c + initial_pq_mean_child + initial_pq_c + (1 | child_id),
  data = merged_data
)

summary(model_h3)
```

**ICC and effect sizes for final model**

```{r RQ3-effect-sizes}
# Intraclass correlation coefficient to examine the proportion of variance explained
performance::icc(model_h3)

# Calculate effect sizes for the linear mixed model, including marginal and conditional R² values, as well as semi-partial R² and f² for each predictor. This provides insight into the variance explained by fixed effects alone and by both fixed and random effects combined.
effect_sizes_h3 <- extract_effect_sizes(model_h3)
effect_sizes_h3$r2_marginal      # variance explained by fixed effects
effect_sizes_h3$r2_conditional   # variance explained by fixed + random effects
effect_sizes_h3$per_predictor    # semi-partial R² and f² per predictor
```

```{r RQ3-visualization-table, message=FALSE}
# Create a summary table of the linear mixed model results for H3, including estimates, standard errors, t-values, p-values, and confidence intervals for each predictor. The table is formatted for publication using the gt package.
table_h3 <- extract_lmm_table(model_h3, c(
  "Intercept" = "Intercept",
  "feedback_conditiondialogic" = "Feedback Condition (Dialogic)",
  "receptivity_c" = "Feedback Receptivity (Centered)",
  "initial_pq_c" = "Initial PQ (Trial-Level)",
  "initial_pq_mean_child" = "Initial PQ (Child-Level)",
  "feedback_conditiondialogic:receptivity_c" = "Feedback Condition × Receptivity"
))
render_lmm_gt(table_h3, caption = "Linear Mixed Model Testing the Moderating Role of Feedback Receptivity on Revised Plan Quality (H3)")
```

<small> *Note.* <i>N</i> = `r n_children_after` children, total observations =
`r n_trials_after` trials. Instructive feedback serves as the reference
category for feedback condition. PQ = Plan Quality. CI = confidence interval; <i>LL</i> =
lower limit; <i>UL</i> = upper limit. 
R²m =`r fmt_bounded(effect_sizes_h3$r2_marginal)`, R²c =
+ `r fmt_bounded(effect_sizes_h3$r2_conditional)`.
</small>


# Additional Analyses

## Robustness Check RQ1: Ordinal Multilevel Logistic Regression

**Planned Analysis:** Given the non-normal distribution of the plan
quality scores and the presence of floor and ceiling effects, an ordinal
multilevel logistic regression model will be fitted as a robustness
check. The dependent variable will be the revised plan quality score
(0-5), treated as an ordinal outcome. The model will include feedback
condition, initial plan quality, and their interaction as fixed effects,
with random intercepts for child and trial to account for the repeated
measures design and potential variability across trials. The
significance of the fixed effects will be examined to determine if the
results are consistent with those obtained from the linear mixed model.

**CLMM Results of Assumption Testing**

- Independence of observations: Random Intercept (1 \| child_id) to
  account for repeated measures within children. ✓
- Proportional odds ✓
- No perfect separation ✓
- No Multicollinearity ✓ 
- *Conclusion:* Data meets assumptions for analysis

```{r data-preparation-robust-RQ1, include=FALSE}
# Prepare data for ordinal multilevel logistic regression by selecting relevant columns, reshaping the data to long format, and converting variables to appropriate types (factor and ordered). This prepares the dataset for fitting a cumulative link mixed model (CLMM) to analyze the effects of feedback condition and time point on plan quality.
ordinal_data <- merged_data |> 
  select(child_id, trial_id, feedback_condition, initial_pq, revised_pq) |> 
  pivot_longer(
    cols = c(initial_pq, revised_pq),
    names_to = "time_point",
    values_to = "plan_quality"
  ) |> 
  mutate(
    time_point = factor(
      ifelse(time_point == "initial_pq", "Pre-Feedback", "Post-Feedback"),
      levels = c("Pre-Feedback", "Post-Feedback")
    ),
    feedback_condition = factor(
      feedback_condition,
      levels = c("instructive", "dialogic"),
      labels = c("instructive Feedback", "dialogic Feedback")
    ),
    plan_quality = ordered(plan_quality)
  )
```

Fit a cumulative link mixed model (CLMM) to analyze the effects of feedback condition and time point on plan quality, with random intercepts for child to account for repeated measures. The model uses a logit link function to estimate the odds of higher plan quality scores based on the fixed effects of feedback condition and time point.

```{r robust-RQ1-analysis, results='hide', echo=TRUE}
clmm_model <- clmm(
  plan_quality ~ feedback_condition * time_point + (1 | child_id),
  data = ordinal_data,
  link = "logit"
)
```


```{r robust-RQ1-visualization, tab.cap="Cumulative Link Mixed Model of Plan Quality as a Function of Feedback Condition and Time Point (Robustness Check for H1)"}
# Render the results of the cumulative link mixed model (CLMM) for plan quality in a publication-ready table format using the gt package. The table includes estimates, odds ratios, confidence intervals, and p-values for each predictor in the model, with appropriate labels and formatting for clarity.
extract_clmm_table <- function(model) {
  coefs  <- summary(model)$coefficients
  ci_all <- confint(model, type = "Wald")

  stars <- dplyr::case_when(
    coefs[, "Pr(>|z|)"] < .001 ~ "***",
    coefs[, "Pr(>|z|)"] < .01  ~ "**",
    coefs[, "Pr(>|z|)"] < .05  ~ "*",
    TRUE ~ ""
  )

  tibble(
    Variable = rownames(coefs),
    Estimate = paste0(
      fmt(exp(coefs[, "Estimate"])),
      ifelse(stars == "", "", paste0("", stars, ""))
    ),
    CI = paste0(fmt(exp(ci_all[, 1])), " – ", fmt(exp(ci_all[, 2]))),
    Group = if_else(grepl("\\|", rownames(coefs)), "Thresholds", "Fixed Effects")
  )
}

clmm_term_labels <- c(
  "0|1" = "0|1",
  "1|2" = "1|2",
  "2|3" = "2|3",
  "3|4" = "3|4",
  "4|5" = "4|5",
  "feedback_conditiondialogic Feedback" = "Feedback Condition (Dialogic)",
  "time_pointPost-Feedback" = "Time (Post-Feedback)",
  "feedback_conditiondialogic Feedback:time_pointPost-Feedback" = "Feedback Condition × Time"
)

table_clmm <- extract_clmm_table(clmm_model) |>
  dplyr::mutate(Effect = dplyr::coalesce(unname(clmm_term_labels[Variable]), Variable)) |>
  dplyr::select(Effect, Estimate, CI, Group)


extract_tau00_clmm <- function(model) {
  tau00 <- tryCatch({
    vc  <- as.data.frame(VarCorr(model))
    val <- vc$vcov[vc$grp == "child_id"]
    if (length(val) == 1) val else NA_real_
  }, error = function(e) NA_real_)

  if (length(tau00) == 0 || is.na(tau00)) {
    tau00 <- tryCatch({
      val <- as.numeric(model$ST[[1]])^2
      if (length(val) == 1) val else NA_real_
    }, error = function(e) NA_real_)
  }
  tau00
}

sigma2_logit <- pi^2 / 3
tau00        <- extract_tau00_clmm(clmm_model)
r2_clmm      <- tryCatch(performance::r2_nakagawa(clmm_model), error = function(e) NULL)

random_part <- tibble(
  Effect = c("σ²", "τ₀₀ (child_id)"),
  Estimate = c(fmt(sigma2_logit), if (is.na(tau00)) "NA" else fmt(tau00)),
  CI = "",
  Group = "Random Effects"
)

if (!is.na(tau00)) {
  icc_clmm <- tau00 / (tau00 + sigma2_logit)
  random_part <- dplyr::bind_rows(random_part, tibble(
     Effect = "ICC", Estimate = fmt_bounded(icc_clmm), CI = "", Group = "Random Effects"
  ))
}

if (!is.null(r2_clmm)) {
  random_part <- dplyr::bind_rows(random_part, tibble(
    Effect = "R² (marginal / conditional)",
    Estimate = paste0(fmt_bounded(r2_clmm$R2_marginal), " / ", fmt_bounded(r2_clmm$R2_conditional)),
    CI = "", Group = "Random Effects"
  ))
}

table_clmm_full <- dplyr::bind_rows(table_clmm, random_part) |>
  dplyr::mutate(Group = factor(Group, levels = c("Thresholds", "Fixed Effects", "Random Effects")))

table_clmm_full |>
  gt(rowname_col = "Effect", groupname_col = "Group") |>
  tab_caption(caption = "Cumulative Link Mixed Model of Plan Quality as a Function of Feedback Condition and Time Point (Robustness Check for H1)") |>
  tab_spanner(label = "Plan Quality", columns = c(Estimate, CI)) |>
  cols_label(Estimate = md("*Odds Ratio*"), CI = md("*95% CI*")) |>
  text_transform(
    locations = cells_body(columns = Estimate),
    fn = function(x) purrr::map(x, gt::html)
  ) |>
  cols_align(align = "center", columns = c(Estimate, CI)) |>
  cols_width(Effect ~ px(260), everything() ~ px(140)) |>
  opt_table_font(font = "Times New Roman") |>
  tab_style(style = cell_text(indent = px(20), align = "left"), locations = cells_stub()) |>
  tab_source_note(source_note = "* p < .05. ** p < .01. *** p < .001.") |>
  tab_options(
    data_row.padding = px(8),
    column_labels.border.top.style = "solid", column_labels.border.top.width = px(1),
    column_labels.border.top.color = "black",
    column_labels.border.bottom.style = "solid", column_labels.border.bottom.width = px(1),
    column_labels.border.bottom.color = "black",
    table_body.border.bottom.style = "solid", table_body.border.bottom.width = px(1),
    table_body.border.bottom.color = "black",
    stub.border.style = "none"
  )
```


## Distribution of Plan Quality across Trials

As there appear to be large individual differences, the next step will
be to examine how the quality of the plans varies across the trials as
possible explanatory factor.


```{r plan-quality-across-trials, fig.cap="Trend in Plan Quality across Trials"}
# Prepare data for visualization by selecting relevant columns, reshaping the data to long format, and recoding time point labels for clarity. This allows for the examination of trends in plan quality across the six trials, facilitating the creation of a line plot to visualize average plan quality and standard errors at each trial and time point.
long_data <- merged_data |> 
  select(child_id, trial_id, initial_pq, revised_pq) |> 
  pivot_longer(cols = c(initial_pq, revised_pq), 
               names_to = "time", 
               values_to = "planquality") |> 
  
  mutate(time = recode_values(time,
                            "initial_pq" ~ "Initial Plan",
                            "revised_pq" ~ "Revised Plan"))

summary_data <- long_data |> 
  group_by(trial_id, time) |> 
  summarise(mean_pq = mean(planquality, na.rm = TRUE),
            se_pq = sd(planquality, na.rm = TRUE) / sqrt(n()), 
            .groups = 'drop')

# Visualize the trends in plan quality across the six trials using ggplot2, with lines representing the mean plan quality for each time point (initial and revised) and error bars indicating standard errors. The x-axis represents trial IDs, while the y-axis shows average plan quality scores.
ggplot(summary_data, aes(x = as.numeric(trial_id), y = mean_pq, color = time, group = time)) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = mean_pq - se_pq, ymax = mean_pq + se_pq), width = 0.1) +
  scale_x_continuous(breaks = 1:6) + 
  # y-axis anchored at 0 for an undistorted comparison of mean plan quality
  scale_y_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0.05))) +
  labs(x = "Trial ID",
       y = "Average plan quality (with standard error)",
       color = "Time") +
  theme_thesis() +
  theme(legend.position = "right")
```

**Inferential Test for Trial ID**

To investigate whether there are significant differences in plan quality across the six trials, a one-way repeated measures analysis of variance (rm-Anova) will be conducted. This analysis will help determine if the trial ID has a statistically significant effect on plan quality, accounting for the repeated measures design where each child contributes multiple observations across trials.

```{r trials-rmAnova, include=FALSE}
# Perform repeated measures ANOVA for initial_pq across trials using the aov_ez function from the afex package. This analysis will assess whether there are significant differences in plan quality based on trial ID, while accounting for the repeated measures design with child_id as the subject identifier.
anova_initial <- aov_ez(id = "child_id",
                        dv = "initial_pq",
                        within = "trial_id",
                        data = merged_data)

summary(anova_initial)

# Mauchly's test for sphericity, and the Greenhouse-Geisser/Huynh-Feldt epsilon and corrected p-values.
summary(anova_initial)$sphericity.tests
summary(anova_initial)$pval.adjustments
gg_eps_initial <- summary(anova_initial)$pval.adjustments[1, "GG eps"]

pairs(emmeans(anova_initial, "trial_id"), adjust = "bonferroni")

# Perform repeated measures ANOVA for revised_pq across trials using the aov_ez function from the afex package. This analysis will assess whether there are significant differences in plan quality based on trial ID, while accounting for the repeated measures design with child_id as the subject identifier.
anova_revised <- aov_ez(id = "child_id",
                       dv = "revised_pq",
                       within = "trial_id",
                       data = merged_data)

summary(anova_revised)

summary(anova_revised)$sphericity.tests
summary(anova_revised)$pval.adjustments
gg_eps_revised <- summary(anova_revised)$pval.adjustments[1, "GG eps"]

pairs(emmeans(anova_revised, "trial_id"), adjust = "bonferroni")
```

```{r trial-anova-initial-table}
# Extract Anova results for initial_pq. F, p, and ges are already Greenhouse-Geisser corrected by afex whenever sphericity is violated; the epsilon (GG) column below makes that correction visible (see trials-rmAnova for the underlying Mauchly's test).
anova_initial_summary <- as.data.frame(anova_initial$anova_table) |>
  tibble::rownames_to_column("Effect") |>
  dplyr::transmute(
    Effect,
    `$df$` = paste(fmt(`num Df`, digits = 0), fmt(`den Df`, digits = 0), sep = ", "),
    `$F$` = fmt(`F`),
    `$p$` = format_p(`Pr(>F)`),
    `$\\eta^2_G$` = fmt(ges, digits = 2),
    `$\\varepsilon_{GG}$` = fmt(gg_eps_initial, digits = 2)
  ) |>
  dplyr::select(Effect, `$df$`, `$F$`, `$p$`, `$\\eta^2_G$`, `$\\varepsilon_{GG}$`)


kableExtra::kbl(
  anova_initial_summary,
  caption = "Repeated Measures Anova for Initial Plan Quality across Trials"
) |>
  kable_classic(full_width = FALSE, html_font = "Times New Roman") |>
  column_spec(1:5, extra_css = "padding: 10px;") |>
  row_spec(0, extra_css = "text-align: center;")
```

*Note.* Results are based on a one-way repeated measures analysis of
variance evaluating the effect of trial ID on initial plan quality.
Because trial_id has 6 levels, Mauchly's test for sphericity was
conducted, *W* = `r fmt(summary(anova_initial)$sphericity.tests[1, "Test statistic"])`,
*p* `r format_p(summary(anova_initial)$sphericity.tests[1, "p-value"])`; *F*, *p*, and η²_G are Greenhouse-Geisser corrected wherever
sphericity was violated (ε < 1), as reflected in the ε (GG) column.


```{r trial-anova-revised-table}
# Extract Anova results for revised_pq. F, p, and ges are already Greenhouse-Geisser corrected by afex whenever sphericity is violated; the epsilon (GG) column below makes that correction visible instead of implicit (see trials-rmAnova for the underlying Mauchly's test).
anova_revised_summary <- as.data.frame(anova_revised$anova_table) |>
  tibble::rownames_to_column("Effect") |>
  dplyr::transmute(
    Effect,
    `$df$` = paste(fmt(`num Df`, digits = 0), fmt(`den Df`, digits = 0), sep = ", "),
    `$F$` = fmt(`F`),
    `$p$` = format_p(`Pr(>F)`),
    `$\\eta^2_G$` = fmt(ges, digits = 2),
    `$\\varepsilon_{GG}$` = fmt(gg_eps_revised, digits = 2)
  ) |>
  dplyr::select(Effect, `$F$`, `$df$`, `$p$`, `$\\eta^2_G$`, `$\\varepsilon_{GG}$`)

kableExtra::kbl(
  anova_revised_summary,
  caption = "Repeated Measures Anova for Revised Plan Quality across Trials"
) |>
  kable_classic(full_width = FALSE, html_font = "Times New Roman") |>
  column_spec(1:5, extra_css = "padding: 10px;") |>
  row_spec(0, extra_css = "text-align: center;")
```

*Note.* Results are based on a one-way repeated measures analysis of
variance evaluating the effect of trial ID on revised plan quality.
Because trial_id has 6 levels, Mauchly's test for sphericity was
conducted, *W* = `r fmt(summary(anova_revised)$sphericity.tests[1, "Test statistic"])`,
*p* `r format_p(summary(anova_revised)$sphericity.tests[1, "p-value"])`; *F*, *p*, and η²_G are Greenhouse-Geisser corrected wherever sphericity was violated (ε < 1), as reflected in the ε (GG) column.

## Distribution of Plan Quality across Scenarios

The next step will be to examine how the quality of the plans varies across the scenarios as possible explanatory factor. 

```{r plan-quality-across-scenarios, fig.cap="Plan Quality across Scenarios"}
summary_data_scenario <- long_data |>
  left_join(merged_data |> select(child_id, trial_id, scen_id, scen_name),
            by = c("child_id", "trial_id")) |>
  group_by(scen_name, time) |>
  summarise(mean_pq = mean(planquality, na.rm = TRUE),
            se_pq = sd(planquality, na.rm = TRUE) / sqrt(n()),
            .groups = 'drop')

ggplot(summary_data_scenario, aes(x = scen_name, y = mean_pq, color = time, group = time)) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = mean_pq - se_pq, ymax = mean_pq + se_pq), width = 0.1) +
  scale_y_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0.05))) +
  labs(x = "Scenario",
       y = "Average plan quality (with standard error)",
       color = "Time") +
  theme_thesis() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1),
        plot.margin = margin(t = 5.5, r = 5.5, b = 5.5, l = 20)) +
  coord_cartesian(clip = "off") +
  theme(legend.position = "right")
```

**Inferential Test for Scenario ID**

```{r scenario-rmAnova, include=FALSE}
# Perform repeated measures ANOVA for initial_pq across scenarios using the aov_ez function from the afex package. This analysis will assess whether there are significant differences in plan quality based on scenario id, while accounting for the repeated measures design with child_id as the subject identifier.
anova_initial_scenario <- aov_ez(id = "child_id",
                                  dv = "initial_pq",
                                  within = "scen_id",
                                  data = merged_data)

summary(anova_initial_scenario)

summary(anova_initial_scenario)$sphericity.tests
summary(anova_initial_scenario)$pval.adjustments
gg_eps_initial_scenario <- summary(anova_initial_scenario)$pval.adjustments[1, "GG eps"]

pairs(emmeans(anova_initial_scenario, "scen_id"), adjust = "bonferroni")
```


```{r scenario-anova-initial-table}
# Extract ANOVA results for initial_pq. F, p, and ges are already Greenhouse-Geisser corrected by afex whenever sphericity is violated; the epsilon (GG) column below makes that correction visible (see scenario-rmAnova for the underlying Mauchly's test).
anova_initial_scenario_summary <- as.data.frame(anova_initial_scenario$anova_table) |>
  tibble::rownames_to_column("Effect") |>
  dplyr::transmute(
    Effect,
    `$df$` = paste(fmt(`num Df`, digits = 0), fmt(`den Df`, digits = 0), sep = ", "),
    `$F$` = fmt(`F`),
    `$p$` = format_p(`Pr(>F)`),
    `$\\eta^2_G$` = fmt(ges, digits = 2),
    `$\\varepsilon_{GG}$` = fmt(gg_eps_initial_scenario, digits = 2)
  ) |>
  dplyr::select(Effect, `$df$`,`$F$`, `$p$`, `$\\eta^2_G$`, `$\\varepsilon_{GG}$`)

kableExtra::kbl(
  anova_initial_scenario_summary,
  caption = "Repeated Measures Anova for Initial Plan Quality across Scenarios"
) |>
  kable_classic(full_width = FALSE, html_font = "Times New Roman") |>
  column_spec(1:5, extra_css = "padding: 10px;") |>
  row_spec(0, extra_css = "text-align: center;")
```

*Note*. Results are based on a one-way repeated measures analysis of variance evaluating the effect of scenario ID on revised plan quality.
Because scenario has 6 levels, Mauchly's test for sphericity was conducted, *W* = `r fmt(summary(anova_initial_scenario)$sphericity.tests[1, "Test statistic"])`,
*p* `r format_p(summary(anova_initial_scenario)$sphericity.tests[1, "p-value"])`; *F*, *p*, and η²_G are Greenhouse-Geisser corrected wherever sphericity was violated (ε < 1), as reflected in the ε (GG) column.


## Distribution of Plan Quality by Gender

This analysis is exploratory and was not part of the pre-registered hypotheses H1–H3. 

```{r mixed-anova-gender, include=FALSE}
# Reshape to long format for the mixed ANOVA: time (initial vs. revised plan quality) is the within-subjects factor, gender is the between-subjects factor.
long_data_gender <- merged_data |>
  select(child_id, gender, initial_pq, revised_pq) |>
  pivot_longer(cols = c(initial_pq, revised_pq),
               names_to = "time",
               values_to = "planquality") |>
  mutate(
    time = case_match(time,
                       "initial_pq" ~ "Initial Plan",
                       "revised_pq" ~ "Revised Plan"),
   gender = case_match(as.character(gender),
                       "1" ~ "Male", 
                       "2" ~ "Female", 
                      "3" ~ "Other",
                     .default = as.character(gender)) |>
  factor() |>
  droplevels()
  )


# Mixed ANOVA: time (within) x gender (between) on plan quality. Tests whether the initial-to-revised improvement differs by gender (interaction), in addition to main effects of time and gender.
anova_gender <- aov_ez(id = "child_id",
                        dv = "planquality",
                        within = "time",
                        between = "gender",
                        data = long_data_gender)

summary(anova_gender)

# Follow-up pairwise comparisons, only meaningful to inspect closely if the main effect of gender or the time:gender interaction is significant.
pairs(emmeans(anova_gender, ~ gender | time), adjust = "bonferroni")
pairs(emmeans(anova_gender, ~ time | gender), adjust = "bonferroni")
```


```{r mixed-anova-gender-table}
# Extract all three effects (time, gender, time:gender) in one APA-style table.
anova_gender_summary <- as.data.frame(anova_gender$anova_table) |>
  tibble::rownames_to_column("Effect") |>
  dplyr::transmute(
    Effect,
    `$df$` = paste(fmt(`num Df`, digits = 0), fmt(`den Df`, digits = 0), sep = ", "),
    `$F$` = fmt(`F`),
    `$p$` = format_p(`Pr(>F)`),
    `$\\eta^2_G$` = fmt(ges, digits = 2)
  )

kableExtra::kbl(
  anova_gender_summary,
  caption = "Mixed Anova of Plan Quality by Time and Gender"
) |>
  kable_classic(full_width = FALSE, html_font = "Times New Roman") |>
  column_spec(1:5, extra_css = "padding: 10px;") |>
  row_spec(0, extra_css = "text-align: center;")


summary_data_gender <- long_data_gender |>
  group_by(gender, time) |>
  summarise(mean_pq = mean(planquality, na.rm = TRUE),
            se_pq = sd(planquality, na.rm = TRUE) / sqrt(n()),
            .groups = 'drop')
```

<small> *Note.* Results are based on a 2 (Time: initial vs. revised plan quality) × 2 (Gender: male, female) mixed-design ANOVA, with time as the within-subjects factor and gender as the between-subjects factor. The "other" gender category was not represented in the analytic sample (*n* = 0) and was therefore automatically dropped from the model. Because the within-subjects factor has only two levels, the sphericity assumption is trivially met and no Greenhouse-Geisser correction was required. </small>


```{r mixed-anova-gender-figure, fig.cap="Mixed Anova of Plan Quality"}
ggplot(summary_data_gender, aes(x = time, y = mean_pq, color = gender, group = gender)) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = mean_pq - se_pq, ymax = mean_pq + se_pq), width = 0.1) +
  scale_y_continuous(limits = c(0, NA), expand = expansion(mult = c(0, 0.05))) +
  labs(x = "Time",
       y = "Average plan quality (with standard error)",
       color = "Gender") +
  theme_thesis() +
  theme(legend.position = "right")
```
<small> *Note.* Points represent estimated means of plan quality by time point (initial vs. revised) and gender; error bars indicate ±1 *SE*. </small>

- Plan quality improved substantially from the initial to the revised plan for both genders, *F*(`r fmt(anova_gender$anova_table["time", "num Df"], 0)`, `r fmt(anova_gender$anova_table["time", "den Df"], 0)`) = `r fmt(anova_gender$anova_table["time", "F"])`, *p* `r format_p(anova_gender$anova_table["time", "Pr(>F)"])`, η²_G = `r fmt(anova_gender$anova_table["time", "ges"])`.
- Girls showed higher plan quality than boys at both time points, *F*(`r fmt(anova_gender$anova_table["gender", "num Df"], 0)`, `r fmt(anova_gender$anova_table["gender", "den Df"], 0)`) = `r fmt(anova_gender$anova_table["gender", "F"])`, *p* `r format_p(anova_gender$anova_table["gender", "Pr(>F)"])`, η²_G = `r fmt(anova_gender$anova_table["gender", "ges"])`, but the two genders improved to a comparable extent, as indicated by the non-significant time × gender interaction.


## Robustness Check RQ3

- To examine the robustness of the receptivity scale's internal
  consistency, a reliability analysis was conducted on the four items
  (Cronbach's α). Item-total correlations and alpha-if-item-deleted
  statistics were inspected to identify items reducing scale
  reliability (see Distribution of Receptivity).

```{r robustness-check-RQ3-dropping-item-4, include=FALSE}
# Reliability analysis of the 4-item receptivity scale 

# Confirm improved reliability without Item 4
psych::alpha(merged_data[, c("recep_q1", "recep_q2", "recep_q3")])

# Re-fit H3 with the 3-item receptivity score to assess robustness of the moderation effect
model_h3_robust <- lmerTest::lmer(
  revised_pq ~ feedback_condition * receptivity_3items_c + initial_pq_c + initial_pq_mean_child + (1 | child_id),
  data = merged_data
)
```


```{r robustness-check-RQ3-visualization, tab.cap="Model Comparison Receptivity: Original vs. Robustness Check (3-item)", message=FALSE}
# Render a comparison table of the original linear mixed model (H3) and the robustness check model (H3 with 3-item receptivity score) using gt() styling. The table includes estimates, confidence intervals, and p-values for each predictor in both models, allowing for a side-by-side comparison of the effects of feedback condition and receptivity on revised plan quality.
combine_lmm_tables <- function(models, model_names, term_labels) {
  tables <- purrr::map2(models, model_names, function(model, model_name) {
    extract_lmm_table(model, term_labels) |>
      dplyr::filter(Group == "Fixed Effects") |>
      dplyr::transmute(
        Effect,
        "{model_name}__est" := paste0(Estimate, " [", LL, ", ", UL, "]"),
        "{model_name}__p"   := p
      )
  })

  purrr::reduce(tables, dplyr::full_join, by = "Effect")
}

render_lmm_comparison_gt <- function(table_data, model_names, caption) {
  gt_tab <- table_data |>
    gt(rowname_col = "Effect") |>
    tab_caption(caption = caption) |>
    sub_missing(missing_text = "") |>
    opt_table_font(font = "Times New Roman") |>
    cols_width(Effect ~ px(220), everything() ~ px(150)) |>
    tab_style(
      style = cell_text(align = "center"),
      locations = list(
        cells_column_labels(columns = -Effect),
        cells_body(columns = -Effect)
        )
      ) |>
    
    
    tab_options(
      data_row.padding = px(8),
      column_labels.border.top.style = "solid", column_labels.border.top.width = px(1),
      column_labels.border.top.color = "black",
      column_labels.border.bottom.style = "solid", column_labels.border.bottom.width = px(1),
      column_labels.border.bottom.color = "black",
      table_body.border.bottom.style = "solid", table_body.border.bottom.width = px(1),
      table_body.border.bottom.color = "black",
      stub.border.style = "none"
    )

  for (model_name in model_names) {
    gt_tab <- gt_tab |>
      cols_label(
        !!rlang::sym(paste0(model_name, "__est")) := md("*b* [95% CI]"),
        !!rlang::sym(paste0(model_name, "__p"))   := md("*p*")
      ) |>
      tab_spanner(label = model_name, columns = tidyselect::starts_with(paste0(model_name, "__")))
  }
  gt_tab
}

model_comparison_labels <- c(
  "Intercept" = "Intercept",
  "feedback_conditiondialogic" = "Feedback Condition (Dialogic)",
  "receptivity_c" = "Feedback Receptivity (Centered)",
  "receptivity_3items_c" = "Feedback Receptivity (Centered)",
  "initial_pq_c" = "Initial Plan Quality (Centered)",
  "initial_pq_mean_child" = "Initial Plan Quality (Child Mean)",
  "feedback_conditiondialogic:receptivity_c" = "Feedback Condition × Receptivity",
  "feedback_conditiondialogic:receptivity_3items_c" = "Feedback Condition × Receptivity"
)

table_h3_comparison <- combine_lmm_tables(
  models = list(model_h3, model_h3_robust),
  model_names = c("Original (4-item)", "Robustness check (3-item)"),
  term_labels = model_comparison_labels
)
render_lmm_comparison_gt(
  table_h3_comparison,
  model_names = c("Original (4-item)", "Robustness check (3-item)"),
  caption = "Model Comparison Receptivity: Original vs. Robustness Check (3-item)"
)

```


**Exploratory Analysis**

- As a supplementary robustness check, an exploratory item-level
  moderation analysis was conducted in which each receptivity item was
  entered individually (grand-mean centered) as the moderator in place
  of the composite receptivity score.
- This yielded four parallel models, one per receptivity dimension
  (experiential attitudes, instrumental attitudes, cognitive engagement,
  behavioral engagement).
  


```{r exploratory-RQ3, include=FALSE}
# Exploratory item-level moderation analysis of receptivity: Fit separate linear mixed models for each receptivity item as the moderator, controlling for initial plan quality and including a random intercept for child. The interaction between feedback condition and each receptivity item is examined to assess whether the moderation effect varies across different dimensions of receptivity.
items <- c("recep_q1", "recep_q2", "recep_q3", "recep_q4_r")
item_labels <- c("Experiential Attitudes", "Instrumental Attitudes",
                  "Cognitive Engagement", "Behavioral Engagement")


item_models <- purrr::map(items, function(item) {
  item_c <- paste0(item, "_c")
  f <- as.formula(paste0(
  "revised_pq ~ + initial_pq_c + initial_pq_mean_child + feedback_condition * ", item_c, " + (1 | child_id)"
  ))
  lmerTest::lmer(f, data = merged_data)
  }) |> 
  setNames(item_labels)

purrr::walk(item_models, ~ print(summary(.x)))
```


```{r exploratory-RQ3-table, tab.cap="Exploratory Item-Level Moderation Analysis of Receptivity", message=FALSE}
# Side-by-side comparison of the four exploratory item-level moderation models, rendered with the same gt() pipeline. Each model corresponds to one receptivity item, and the table allows for a direct comparison of the fixed effects across the different dimensions of receptivity.
combine_lmm_tables <- function(models, model_names, term_labels) {
  tables <- purrr::map2(models, model_names, function(model, model_name) {
    extract_lmm_table(model, term_labels) |>
      dplyr::filter(Group == "Fixed Effects") |>
      dplyr::transmute(
        Effect,
        "{model_name}__est" := paste0(Estimate, " [", LL, ", ", UL, "]"),
        "{model_name}__p"   := p
      )
  })

  purrr::reduce(tables, dplyr::full_join, by = "Effect")
}

render_lmm_comparison_gt <- function(table_data, model_names, caption) {
  gt_tab <- table_data |>
    gt(rowname_col = "Effect") |>
    tab_caption(caption = caption) |>
    sub_missing(missing_text = "") |>
    opt_table_font(font = "Times New Roman") |>
    cols_width(Effect ~ px(220), everything() ~ px(150)) |>
     tab_style(
      style = cell_text(align = "center"),
      locations = list(
        cells_column_labels(columns = -Effect),
        cells_body(columns = -Effect)
        )
      ) |>
    tab_options(
      data_row.padding = px(8),
      column_labels.border.top.style = "solid", column_labels.border.top.width = px(1),
      column_labels.border.top.color = "black",
      column_labels.border.bottom.style = "solid", column_labels.border.bottom.width = px(1),
      column_labels.border.bottom.color = "black",
      table_body.border.bottom.style = "solid", table_body.border.bottom.width = px(1),
      table_body.border.bottom.color = "black",
      stub.border.style = "none"
    )

  for (model_name in model_names) {
    gt_tab <- gt_tab |>
      cols_label(
        !!rlang::sym(paste0(model_name, "__est")) := md("*b* [95% CI]"),
        !!rlang::sym(paste0(model_name, "__p"))   := md("*p*")
      ) |>
      tab_spanner(label = model_name, columns = tidyselect::starts_with(paste0(model_name, "__")))
  }
  gt_tab
}

item_model_labels <- c(
  "Intercept" = "Intercept",
  "feedback_conditiondialogic" = "Feedback Condition (Dialogic)",
  "initial_pq_c" = "Initial Plan Quality (Centered)",
  "initial_pq_mean_child" = "Initial Plan Quality (Child Mean)",
  "recep_q1_c" = "Receptivity Item (Centered)",
  "recep_q2_c" = "Receptivity Item (Centered)",
  "recep_q3_c" = "Receptivity Item (Centered)",
  "recep_q4_r_c" = "Receptivity Item (Centered)",
  "feedback_conditiondialogic:recep_q1_c" = "Feedback Condition × Receptivity Item",
  "feedback_conditiondialogic:recep_q2_c" = "Feedback Condition × Receptivity Item",
  "feedback_conditiondialogic:recep_q3_c" = "Feedback Condition × Receptivity Item",
  "feedback_conditiondialogic:recep_q4_r_c" = "Feedback Condition × Receptivity Item"
)

table_item_models <- combine_lmm_tables(
  models = item_models,
  model_names = item_labels,
  term_labels = item_model_labels
)
render_lmm_comparison_gt(
  table_item_models,
  model_names = item_labels,
  caption = "Exploratory Item-Level Moderation Analysis of Receptivity"
)
```

Holm-adjusted p-values to account for multiple comparisons across the four receptivity items.

```{r exploratory-RQ3-holm-table}
# Extract interaction p-values from the item-level moderation models and create a table with Holm-adjusted p-values to account for multiple comparisons. This provides a more conservative assessment of the significance of the interaction effects across the four receptivity items.
interaction_p <- sapply(item_models, function(m) {
  s <- summary(m)$coefficients
  s[grep(":", rownames(s)), "Pr(>|t|)"]
})
tibble(
  Predictor = item_labels,
  `$p$ (raw)` = format_p(interaction_p),
  `$p$ (Holm-adjusted)` = format_p(p.adjust(interaction_p, method = "holm"))
) |>
  knitr::kable(caption = "Holm-Corrected Interaction p-Values for Item-Level Moderation")
```


# Appendix: Model Diagnostics

In the following sections, the assumption checks for each of the analyses are presented. These checks include assessments of linearity, normality of residuals, homoscedasticity, and multicollinearity, as well as checks for the proportional odds assumption in the ordinal model. The results of these diagnostics inform the robustness and validity of the statistical models used in the analyses.

## H1: Linear Mixed Model
```{r RQ1-assumptions}
# Full assumption-check battery for H1 (see helper-function-lmm-assumptions).
check_lmm_assumptions(model_h1, model_label = "Children (H1)")
```

## H2.1: Mediation Model (Perceived Helpfulness)
```{r RQ2-H2-1-assumptions}
# Mediator-Model with cluster control
mod_mediator_help <- lme4::lmer(perct_help_c ~ feedback_dummy + (1 | child_id), data = merged_data)
# Outcome-Model with cluster control and controlling for initial plan quality
mod_outcome_help  <- lme4::lmer(revised_pq ~ feedback_dummy + perct_help_c + initial_pq_c + initial_pq_mean_child + (1 | child_id), data = merged_data)

check_mediation_assumptions(mod_mediator_help, mod_outcome_help)
```

## H2.2: Mediation Model (Perceived Motivation)
```{r RQ2-H2-2-assumptions}
# Mediator-Model with cluster control
mod_mediator_moti <- lme4::lmer(perct_moti_c ~ feedback_dummy + (1 | child_id), data = merged_data)
# Outcome-Model with cluster control and controlling for initial plan quality
mod_outcome_moti  <- lme4::lmer(revised_pq ~ feedback_dummy + perct_moti_c + initial_pq_c + initial_pq_mean_child + (1 | child_id), data = merged_data)

check_mediation_assumptions(mod_mediator_moti, mod_outcome_moti)
```

## H3: Linear Mixed Model with Moderator
```{r RQ3-assumptions, include=FALSE}
# Full assumption-check battery for H3 (see helper-function-lmm-assumptions)
check_lmm_assumptions(model_h3, model_label = "Children (H3)")
```

## Robustness Check RQ1: Ordinal Model
```{r robust-RQ1-assumptions}
# Check for proportional odds assumption using the same fixed-effects structure as clmm_model
po_test <- clm(
  plan_quality ~ feedback_condition * time_point,
  data = ordinal_data
)
po_test_result <- Anova(po_test, type = "III")
print(po_test_result)

# Check for empty cells in the feedback_condition x time_point design against plan_quality, to
# ensure sufficient observations per cell for reliable estimation. Mirrors clmm_model's fixed effects.
contingency_table <- table(
  interaction(ordinal_data$feedback_condition, ordinal_data$time_point),
  ordinal_data$plan_quality
)
empty_cells <- sum(contingency_table == 0)
total_cells <- length(contingency_table)

print("Cross-tabulation for RQ1 Groups (Feedback Condition x Time Point):")
print(contingency_table)

# Check for multicollinearity in the fixed effects of clmm_model (VIF only depends on the predictor
# matrix, so the linear proxy model just needs matching predictors). VIF > 5 indicates a concern.
vif_data_clmm <- ordinal_data |> 
  dplyr::select(plan_quality, feedback_condition, time_point) |> 
  na.omit()
vif_model_clmm <- lm(as.numeric(plan_quality) ~ feedback_condition * time_point, data = vif_data_clmm)
vif(vif_model_clmm)
```

# Session Info

```{r session-info, echo=FALSE}
sessionInfo()
```

```{r extract-tables, include=FALSE}
# Define tables to be extracted and saved as Word documents. Each table is associated with a caption for clarity in the output documents.
tables <- list(
  list(data = descriptives_table, caption = "Descriptive Statistics by Feedback Condition"),
  list(data = table_h1, caption = "Linear Mixed Model (H1)"),
  list(data = table_h2_1, caption = "Mediation Model of Perceived Helpfulness on Plan Quality Revision (H2.1)"), 
  list(data = table_h2_2, caption = "Mediation Model of Perceived Motivation on Plan Quality Revision (H2.2)"), 
  list(data = table_clmm_full, caption = "Results of the Cumulative Link Mixed Model for Plan Quality")
  # weitere Tabellen hier ergänzen
  
)

# Basis path
 path <- here("Tables_and_Figures")

# Loop
for (i in seq_along(tables)) {
  ft <- flextable(tables[[i]]$data) |>
    set_caption(tables[[i]]$caption) |>
    theme_apa() |>
    autofit()

  doc <- read_docx() |>
    body_add_flextable(ft)

  print(doc, target = file.path(path, paste0("tab", i, ".docx")))
  message("Saved: tab", i, ".docx")
}
 
 

 
```

# References

Cohen, J. (1992). A power primer. Psychological Bulletin, 112(1),
155–159. <https://doi.org/10.1037/0033-2909.112.1.155>

Jaeger, B. C., Edwards, L. J., Das, K., & Sen, P. K. (2016). An R2 statistic for fixed effects in the generalized linear mixed model. Journal of Applied Statistics, 44(6), 1086–1105. https://doi.org/10.1080/02664763.2016.1193725

Kuder, G. F., & Richardson, M. W. (1937). The theory of the estimation of test reliability. Psychometrika, 2(3), 151–160. https://doi.org/10.1007/BF02288391

Nakagawa, S., & Schielzeth, H. (2013). A general and simple method for
obtaining R2 from generalized linear mixed-effects models. Methods in
Ecology and Evolution, 4(2), 133–142.
<https://doi.org/10.1111/j.2041-210x.2012.00261.x>

Nunnally, J. C. (1978). Psychometric Theory (2nd ed.). New York:
McGraw-Hill.
